### 2021-04-28 source/tex/manuscript.tex
Finalized edits and phrasing.
Created tex files
sent to HJB for review

%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[british]{achemso}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stackrel}
\usepackage{graphicx}
\usepackage{subscript}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\title{Mechanisms of detachment in fibrillar adhesive systems}

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Hans-J\"{u}rgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\email{kappl@mpip-mainz.mpg.de}

\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\ProvideTextCommand{\~}{LGR}[1]{\char126#1}

\DeclareRobustCommand{\cyrtext}{%
  \fontencoding{T2A}\selectfont\def\encodingdefault{T2A}}
\DeclareRobustCommand{\textcyr}[1]{\leavevmode{\cyrtext #1}}

\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}

\makeatother

\begin{document}
\begin{abstract}
Several creatures can climb on smooth surfaces with the help of hairy
adhesive pads on their legs. A rapid change from strong attachment
to effortless detachment of the leg is enabled by the asymmetric geometry
of the hairs. In this study, we propose possible mechanisms by which
a hairy pad can be easily detached even when the hairs possess no
asymmetry. Based on a spring-based model, we consider three modes
of detachment: vertically pulling the pad while maintaining either
a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
the claw. We show that in all cases, the adhesion force can be significantly
reduced due to elastic forces when the hairs deform non-uniformly
across the array, an effect that we call ``\emph{elastic weakening}''.
Our proposed model illustrates the design advantage provided by hairy
adhesive systems, which not only provides strong adhesion, but also
allows easy detachment, making it suitable as organs for fast locomotion.
The presented approaches can be potentially used to switch the adhesion
state in bio-inspired artificial systems without the need of asymmetric
structures.
\end{abstract}

\section{Introduction}

Over the past few decades, there has been numerous studies to understand
how animals such as geckos and insects are able to walk on surfaces
of any direction while defying gravity. A microscopic observation
reveals that, in many cases, animals have a dense array of hairy structures
at the end of their legs \cite{RN198,RN59}. These hairy adhesive
pads help the animal to stay attached to any surface or detach easily
at will for countless cycles, a property that is referred to as \emph{reversible
adhesion}. Previous attempts to theoretically explain adhesion in
hairy pads\cite{RN40,RN120} has followed two fundamental approaches:
either by energy balance, or by force balance.

In the energy balance approach, adhesion is characterized by ``work
of adhesion'' (W\textsubscript{adh}) which is the energy required
to separate a pad from the surface. During detachment, the elastic
energy stored in the hair is dissipated, which increases W\textsubscript{adh}
and thus adhesion is enhanced\cite{RN29,RN114}. Detachment of an
individual hair can be explained based on Kendall's peeling theory\cite{RN147},
which predicts low forces at high peeling angles.

In the force balance approach, adhesion is characterized by pull-off
force, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
which is the minimum force necessary to separate two surfaces from
contact. Based on a ``cohesive zone model'', Hui et. al.\cite{RN72}
had identified two regimes of single hair detachment: 1) a flaw sensitive
regime, where contact failure occurs due to crack propagation leading
to low \textgreek{sv}\textsubscript{p}, 2) a flaw insensitive regime,
where the contact interface fails simultaneously, leading to high
\textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
that the ``spatula'' shaped hair tips in a gecko's toe allows it
to change adhesion by three orders of magnitude by laterally sliding
and controlling the pulling angle to disorient the hairs. Federle\cite{RN20}
had further argued that the curved shape of the hair helps the pad
to stay attached when pulled proximally, and easily detached by elastic
recoil when pushed distally.

The theories presented so far suggests that low detachment force of
a hairy pad can be attained by 1) increasing the stress concentration
by peeling the pad at high angles, or 2) laterally shearing the pad
before pull-off, which requires the hairs to have an asymmetric geometry
or curvature. However, some insects like male dock beetles predominantly
possess flat ``mushroom'' tipped hairs on their pads\cite{RN19},
which are relatively less asymmetric compared to the ``spatula''
tipped hairs. This begs the question of how the beetle can still easily
detach their legs during locomotion, since these mushroom shaped hairs
should be resilient to detachment via lateral shearing. Artificial
micro-pillar adhesives mimicking the mushroom shaped hairs of the
beetle have in fact demonstrated its superior adhesive strength in
comparison to other geometries\cite{RN112,RN57}. Introducing asymmetry
into the pillar geometry of such mimics for easy detachment is however
challenging due to current limitations in fabrication techniques and
difficulty in scaling-up for practical applications \cite{RN57}.
Alternate strategies are thus desired to switch the adhesion state
of symmetric pillar arrays in a reversible manner, e.g. by buckling
the pillars under compressive load leading to their contact loss \cite{RN279}
or by using special materials reacting to external stimuli such as
magnetic field\cite{RN186}, UV light \cite{RN280} or temperature\cite{RN281}.

In this work, we propose the possible mechanisms by which adhesive
pads with symmetric hairs can be easily detached under a theoretical
framework. The hairy pad is modelled as an array of springs and the
force-balance approach is used to quantify the net adhesion \cite{RN117}.
We hope our work to provide strategies to control the adhesion force
of an artificial micro-pillar adhesive, which has applications in
bio-inspired climbing robots, pick-and-place operations and reusable
adhesives.

\section{Model}

The hairy pad is assumed to be a one dimensional array of $N_{t}$
hairs, each behaving like a spring with spring constant, $k_{h}$,
and natural length, $l_{h,0}$ (Figure \ref{fig:Schematic}). The
array backing is assumed to be stiff. The pad is attached to a linearly
deformable leg, assumed to be another spring with spring constant,
$k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
array at a distance, $s$, from the right end of the array. The hinge
is at a vertical distance, $d_{s}$, from the surface. The hairs are
spaced apart by a width, $w$, and the array is of length, $L=\left(N_{t}-1\right)w$.
The pad is oriented at an angle, $\theta$, while making contact with
a flat smooth surface. Each hair can attain a maximum length, $l_{h,p}$,
before pull-off, such that its pull-off force, $f_{p}=k_{h}\left(l_{h,p}-l_{h,0}\right)$.
$F_{net}$ is the net force on the pad and $M_{net}$ is the the net
torque about the hinge, at a particular instant during the detachment
process.

\begin{figure}[H]
\includegraphics{Figure1-model_schematic}\caption{Spring contact model of a hairy adhesive pad. The pad consists of
an array of $N_{t}$ hairs connected to a deformable leg at the hinge.
At a particular distance, $d_{s}$, $n$ number of hairs are in contact
and the array is oriented at a tilt angle, $\theta$, with the surface.
\label{fig:Schematic}}
\end{figure}

Suppose at a particular instant, there are $n$ hairs in contact with
the surface. The net force on the whole pad will be,

\[
F_{net}=\stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)
\]

Simplifying, we get (see Appendix section for derivation):

\begin{equation}
F_{net}=nk_{h}\left[d_{s}-l_{h,0}-\Psi\sin\theta\right]\label{eq:force_n_d}
\end{equation}

where, $\Psi=s-\frac{n-1}{2}w$. For a particular value of $n$, equation
\ref{eq:force_n_d} is valid until a certain distance, $d_{s,max}$,
above which the left most hair will detach. Just before detachment,
this hair will be at its maximum length, $l_{h,p}$. From simple geometry
we can thus find:

\begin{equation}
d_{s,max}=l_{h,0}+\frac{f_{p}}{k_{h}}+\left[s-\left(n-1\right)w\right]\sin\theta\label{eq:d_max}
\end{equation}

Equation \ref{eq:force_n_d} will be valid for $d_{s}\leq d_{s,max}$.

The maximum possible adhesion of the array would be the case when
all hairs detach simultaneously ($\theta=0\lyxmathsym{\textdegree}$):

\begin{equation}
F_{max}=N_{t}f_{p}\label{eq:simul_detach}
\end{equation}

The net torque, $M_{net}$, about the hinge can be similarly derived
(see Appendix):

\begin{equation}
M_{net}=nk_{h}\cos\theta\left[\left(d_{s}-l_{h,0}\right)\Psi-\left\{ \Psi^{2}+\frac{n^{2}-1}{12}w^{2}\right\} \sin\theta\right]\label{eq:moment_n_d}
\end{equation}

Let us now consider the scenario where even the leg above the hinge
can undergo elastic stretching together with the hairs. When a hair
detaches from the surface, the leg undergoes an elastic recoil due
to the stored elastic energy. Suppose the leg relaxes upward by a
recoil length, $\Delta l$. For $n$ hairs in contact, the force balance
before and after a hair detaches is given respectively by:

\[
\begin{array}{c}
\stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)=k_{l}\left(l_{l}-l_{l,0}\right)\\
\stackrel[i=1]{n-1}{\sum}k_{h}\left(l_{h,i}+\Delta l-l_{h,0}\right)=k_{l}\left(l_{l}-\Delta l-l_{l,0}\right)
\end{array}
\]

Solving the above two equations for $\Delta l$, we get:

\begin{equation}
\Delta l=\frac{f_{p}}{k_{h}\left(n-1\right)+k_{l}}\label{eq:backing_deform}
\end{equation}

Thus, $d_{s}$ shifts by $\Delta l$ in equations \ref{eq:force_n_d}
and \ref{eq:moment_n_d} at each event of hair detachment (i.e. when
$d_{s}=d_{s,max}$).

We express the forces and distances in non-dimensional forms, as below:

\[
\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{w}
\]

Here, $\hat{f_{p}}$ is a parameter which encapsulates the hair's
adhesion force, stiffness and array density. Unless specified, positive
force values represent attraction by convention.

\section{Detachment mechanisms}

We consider three possible mechanisms to detach the adhesive pad from
a surface: 1) \emph{Fixed pull}, where the pad is pulled vertically
up while keeping a fixed leg-hinge, 2) \emph{Free pull,} where the
pad is pulled vertically up while keeping the leg-hinge free to allow
rotation of the array and 3) \emph{Flex}, where the pad is hinged
to an external point (claw-hinge), and detached in a rotary fashion,
emulating the claw function in insects. To investigate each case in
detail, let us assume a pad with $N_{t}=25$ hairs and $\hat{f_{p}}=0.1$
attached to a stiff leg ($k_{l}\rightarrow\infty$). The situation
of a soft leg ($k_{l}/k_{h}=10$) is also considered for the first
two cases involving vertical detachment.

\subsection{Fixed pull}

\begin{figure}[H]
\includegraphics{Case1-Fixed_pull}\caption{Force distance curves for a hairy pad, pulled vertically upwards with
a fixed hinge between the pad and the leg (\emph{Fixed pull}). The
tilt angle, $\theta$, of the array is kept fixed during detachment.
The leg is either stiff ($k_{l}\rightarrow\infty$) or soft ($k_{l}/k_{h}=10$).
Positive force values represent attraction. The green dashed line
represents the maximum possible adhesion for the pad. All values are
normalized to dimensionless forms, as described in text.\label{fig:Fixed-pull}}
\end{figure}

The hairy adhesive pad can be detached by pulling it vertically upwards
while maintaining a constant tilt angle, $\theta$, with the surface.
This can be achieved if the joint connecting the leg to the array
(leg-hinge) is kept fixed. Equations \ref{eq:force_n_d}, \ref{eq:d_max}
and \ref{eq:simul_detach} can be used to get the resulting force-distance
curves.

Increasing the tilt of the pad decreases its maximum force or adhesion
(Figure \ref{fig:Fixed-pull}). Tilting the pad causes an inhomogeneous
deformation of hairs, where, on one end they are stretched, while,
on the other end they are compressed. The balance of the respective
attractive and repulsive elastic forces of the hairs ultimately results
in a decrease in the net force. The tilted orientation also causes
the individual hairs to detach distinctly rather than simultaneously,
further reducing the net adhesive power of the array. We term this
effect of loss in adhesion due to a non-uniform hair deformation across
the array as ``\emph{elastic weakening}''. When there is no tilt
($\theta=0\lyxmathsym{\textdegree}$), all the hairs undergo identical
deformation and ultimately detaches simultaneously after a distance,
$\hat{d_{s}}=0.1$. Here, no \emph{elastic weakening} occurs and the
pad shows the maximum possible adhesion.

For the case of a stiff leg, we see that at small distances, all hairs
of the pad are in contact with the surface, resulting in a linear
force response. On further pulling, the hairs will start to detach
sequentially from left to right, indicated by a characteristic ``saw-tooth''
jitter in the force curves. The hairs of the pad with a higher tilt
angle will start to detach first, followed by the ones with a lower
tilt.

For the case of a soft leg, we observe a similar effect of tilt angle
on the force curves as before. The maximum adhesion force at a particular
tilt is the same as that for the stiff leg. The saw-tooth jitter are
however minimized due to the leg's deformation, leading to a ``dampened''
force response. Interestingly, the force abruptly drops to zero for
the angles $0.2\lyxmathsym{\textdegree}$ and $0.4\lyxmathsym{\textdegree}$.
This is an effect of the elastic recoil of the leg while each hair
loses contact during the detachment process (equation \ref{eq:backing_deform}).
The length difference between the detached hair just before it breaks
contact and its adjacent hair is $w\sin\theta$. If the leg's recoil
length, $\Delta l>w\sin\theta$, the adjacent hair will be stretched
more than its maximum length ($l_{h,p}$), and thus will also detach,
leading to further recoil of the leg. Equation \ref{eq:backing_deform}
shows that $\Delta l$ increases with every subsequent loss of hair
contact if $\theta$ is kept constant. This implies that, once initiated,
the leg's recoil will always be large enough to detach every remaining
hair, resulting in a spontaneous propagation of the detachment front
until the pad completely breaks contact with the surface.

\subsection{Free pull}

\begin{figure}[H]

\includegraphics{Case2-Free_pull}\caption{Force distance curves for a hairy pad, pulled vertically upwards with
a free hinge between the pad and the leg (\emph{Free pull}). $s$
is the distance between the leg-hinge and the right end of the array
and $L$ is the array length. The free hinge allows further tilting
of the array during the vertical pull. The leg is either stiff ($k_{l}\rightarrow\infty$)
or soft ($k_{l}/k_{h}=10$). Positive force values represent attraction.
The green dashed line represents the maximum possible adhesion for
the pad. All values are normalized to dimensionless forms, as described
in text. \label{fig:Free-pull}}

\end{figure}

Similar to the previous case, we once again consider the situation
where the adhesive pad is pulled vertically upwards for detachment.
However now, the leg-hinge is assumed to be free. In this case, the
array will reorient itself to maintain a zero net torque about the
leg-hinge during the entire detachment process. At any given instant,
the tilt angle, $\theta$, can be found by setting $M_{net}$ to zero
in equation \ref{eq:moment_n_d} to get:

\begin{equation}
\theta\left(\hat{d}_{s},n\right)=\arcsin\left[\frac{\left(\hat{s}-\frac{n-1}{2}\right)\hat{d}_{s}}{\left(\hat{s}-\frac{n-1}{2}\right)^{2}+\frac{n^{2}-1}{12}}\right]\label{eq:theta_free_pull}
\end{equation}

Using the above relation together with equations \ref{eq:force_n_d},
\ref{eq:d_max} and \ref{eq:simul_detach}, we can find force-distance
curves during a free vertical pull of the adhesive pad. Since the
position of the leg-hinge will influence the net torque, we use the
ratio, $s/L$, to study its effect on the detachment forces.

Maximum adhesion is seen when the leg-hinge is positioned at the centre
of the array, i.e. $s/L=0.5$ (Figure \ref{fig:Free-pull}). Here,
the net torque due to the hairs is balanced by symmetry and the array
remains parallel to the substrate until all hairs detach simultaneously
at $\hat{d_{s}}=0.1$. Shifting the position of the leg-hinge further
away from the array centre leads to lower forces or adhesion. The
resulting torque imbalance will tilt the array, which reduces the
net force due to the \emph{elastic weakening} effect, as described
in the previous section. Higher $s/L$ increases the net torque to
be balanced, leading to a higher tilt of the array and thus lower
net force.

The force curves look qualitatively different compared to the previous
case of \emph{fixed pull}. A sharp maxima is seen, coinciding with
the point when the first hair detaches. Beyond this, the force starts
to decrease sharply and once again shows the characteristic saw-tooth
jitter as the subsequent hairs detach in sequence. Nearly identical
trend is seen for both a stiff and a soft leg. The elastic recoil
of the leg does slightly reduce the amplitude of the jitter for the
soft leg case. However, no abrupt drop in the force is seen like before.
As the hairs detach, the array gets tilted more and more, making it
less likely for the recoil length, $\Delta l$, to exceed $w\sin\theta$
and detach the next adjacent hair. Thus here, we don't see any propagation
of the detachment front when the leg is soft.

\subsection{Flex}

\begin{figure}[H]
\includegraphics{Case3-Fixed_flex}\caption{Force curves for a hairy pad detached by flexing it about the claw.
$\hat{F}_{pull}=\frac{F_{pull}}{k_{h}w}$ is the normalised pulling
force necessary to apply the torque about the claw-hinge for detachment,
$\hat{F}_{hinge}=\frac{F_{hinge}}{k_{h}w}$ is the normalised reaction
force on the claw-hinge, $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ is
the normalized vertical distance of the claw-hinge from the surface.
Here, $s_{l}/L=1$ and $s_{h}/w=10$. The green dashed line represents
the maximum possible adhesion for the pad. \label{fig:Flex}}
\end{figure}

Instead of a vertical pull, the adhesive pad can also be detached
by rotating it about the claw-hinge, located outside the array. Such
a mode of detachment will be driven by a torque applied by the leg
to rotate the pad around the claw-hinge until all the hairs lose contact.
Let $s_{h}$ be the distance between the claw-hinge and the right
end of the array; $s_{l}$ be the distance between the fixed leg-hinge
and the right end of the array. To illustrate the mechanism, let us
fix $s_{l}/L=1$ and $s_{h}/w=10$ and vary the vertical claw-hinge
distance, $d_{s}$. At any particular instant, the pulling force applied
by the leg, $F_{pull}=M_{net}/\left(s_{l}+s_{h}\right)$, where $M_{net}$
is obtained by setting $s=-s_{h}$ in equation \ref{eq:moment_n_d}.
Equation \ref{eq:force_n_d} will give us the reaction force acting
on the claw-hinge, $F_{claw-hinge}$.

Decreasing the vertical claw-hinge distance reduces the pulling force
necessary to undergo detachment by flexing (Figure \ref{fig:Flex}).
One can imagine that initially, when the array is parallel to the
surface, a lower value of $d_{s}$ means the hairs are in a more compressed
state. When the pad is subsequently rotated around the claw-hinge,
the tilted array will once again lead to an \emph{elastic weakening}
effect due to the inhomogeneous deformation of hairs. This results
in a decrease in the net torque and thus lower $F_{pull}$ for smaller
values of $d_{s}$. $F_{pull}$ can be further reduced of course by
increasing the lever arm ($s_{l}+s_{h}$).

Detachment by flexing requires that the claw remains fixed and stable
during the process. We see that generally, the normal load, acting
on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$.
For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
implying that the claw should adhere well with the surface to resist
this negative load. As the detachment progresses however, the array
starts to exert a positive load on the claw.

\section{Discussion}

In order to characterize how a particular detachment mechanism influences
the adhesion of the pad, we introduce a parameter, \emph{reduction
factor}, defined as:

\begin{equation}
r=\frac{N_{t}f_{p}}{F_{adh}}\label{eq:reversib}
\end{equation}

Here, $F_{adh}$ is the adhesion force required to detach the pad
from the surface following a given mechanism and $N_{t}f_{p}$ is
the maximum possible adhesion of the pad (equation \ref{eq:simul_detach}).
Reduction factor, $r$, represents the extent to which the adhesion
can be reduced by choosing the mode of detachment. A large value of
$r$ implies that adhesion can be reduced by a greater factor, and
this mode is more suitable to easily detach.

\paragraph{Effect of $\hat{f}_{p}$:}

The dimensionless parameter, $\hat{f}_{p}=\frac{f_{p}}{k_{h}w}$,
governs the strength and compliance of the array, where, high values
represent a dense array of strongly adhering soft hairs. Let us consider
the case of an adhesive pad with $N_{t}=25$ hairs and look at how
$\hat{f}_{p}$ influences the reduction factor under each mode of
detachment (Figure \ref{fig:Reduction-factor_fp}). From the heat
maps, one can generally say that lower values of $\hat{f}_{p}$ increase
the reduction factor and thus provide a greater possibility of controlling
adhesion.

\begin{figure}[H]
\noindent \includegraphics{Reduction_factor-fp}\caption{Heat maps showing the effect of the dimensionless parameter, $\hat{f}_{p}$,
on the reduction factor for each mode of detachment. Here, we fix
the number of hairs, $N_{t}=25$. All values are normalized to dimensionless
forms, as described in text. \label{fig:Reduction-factor_fp}}
\end{figure}

When detachment follows the \emph{fixed pull} method (Figure \ref{fig:Reduction-factor_fp}),
for a constant $\hat{f}_{p}$, the reduction factor increases with
increasing tilt angle, $\theta$, and then decreases, showing a maximum
$r$ of 25 at an intermediate $\theta$. Higher values of $\hat{f}_{p}$
shifts this maximum point to higher values of $\theta$. This trend
relates to the \emph{elastic weakening} effect discussed before. Smaller
values of $\theta$ bring a proportion of hairs under compression,
reducing the adhesion and thus increasing $r$. On further tilting
the array, eventually the proportion of stretched hairs will overcome
the ones under compression, which ultimately reduces $r$ at high
$\theta$. When the individual hairs show strong adhesion (i.e. for
high $\hat{f}_{p}$), a greater tilt is necessary to bring the net
adhesion of the array down.

For the case of detachment via \emph{free pull}, $\hat{f}_{p}$ has
no influence on the reduction factor. On the other hand, shifting
the position of the leg-hinge further away from the array (i.e. high
$s/L$) results in large values of $r$. In this scenario, the higher
torque exerted by the array leads to a higher tilt, and thus increases
the reduction factor via \emph{elastic weakening}, saturating to the
maximum value of 25.

For detachment by \emph{flexing}, the reduction factor increases for
higher initial compression of hairs (low $\hat{d}_{s}$). The pad
notably shows a much higher reduction factor at low values of $\hat{f}_{p}$
and $\hat{d}_{s}$, with values as high as 100. Since this mode of
detachment is driven by torque, the pulling force necessary to provide
the torque can be decreased without any limit simply by having a long
lever arm ($\hat{s}_{l}$). In contrast, for the previous cases of
\emph{free pull} and \emph{fixed pull}, the reduction factor is capped
to the maximum number of hairs in the array ($N_{t}=25$). Here, \emph{elastic
weakening} can only reduce the array's adhesion force from $N_{t}$
hairs down to a single hair.

\paragraph{Effect of $N_{t}$:}

Let us now fix $\hat{f}_{p}=0.1$ and investigate the influence of
the number of hairs, $N_{t}$, on the reduction factor (Figure \ref{fig:Reduction-factor-Nt}).
The heat maps show that high $N_{t}$ increases $r$ irrespective
of the mode of detachment. Under a tilted state, more number of hairs
are compressed when $N_{t}$ is high, which reduces the net adhesion.
This highlights the advantage of having a split contact design found
in many biological systems. Higher number of hairs offer a better
control over adhesion and thus is more suited for reversible attachment
and detachment during locomotion. The specific trends of reduction
factor for each mode of detachment can be understood by similar arguments
of \emph{elastic weakening}, as discussed in the previous section.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-Nt}\caption{Heat maps showing the effect of the number of hairs, $N_{t}$, on
the reduction factor for each mode of detachment. Here, we fix the
dimensionless parameter, $\hat{f}_{p}=0.1$. All values are normalized
to dimensionless forms, as described in text. \label{fig:Reduction-factor-Nt}}
\par\end{centering}
\end{figure}

\paragraph{Detachment pathways:}

Based on the three modes of detachment discussed in the previous sections,
one can think of several strategies to detach a hairy adhesive pad
from the surface. To illustrate this, let us consider the adhesive
system of a dock beetle. The beetle is known to have 3 sets of hairy
pads in each of their legs, each possessing hairs of different geometries.
To keep our analysis simple, we will assume each leg to have only
two pads, with identical hairs of ``mushroom'' geometry. The distal
and proximal pads possess roughly 500 and 1000 hairs, respectively\cite{RN19}.
Assuming the pads to be rectangular arrays of $20\times25$ and $40\times25$
hairs, we can model this as a one-dimensional system of 20 and 40
hairs, respectively, by combining the hairs along the width. Based
on reported measurements\cite{RN79}, the beetle's combined ``hair''
is thus considered to have an effective pull-off force, $f_{p}=0.5\times25=12.5$
\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N/m
. The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
long, spaced $w=10$ \textgreek{m}m apart. The adhesive pad also has
a claw, around 200 \textgreek{m}m long, and the leg is connected roughly
at the end of the proximal pad. This will put $\hat{s}_{h}=20$ and
$s_{l}/L=1$, measured relative to the right end of the distal pad.
The beetle's leg is assumed to possess two joints which could serve
as a hinges for rotation (H\textsubscript{1} and H\textsubscript{2}
in Figure \ref{fig:Detachment-pathways} inset). The claw can be used
as an external hinge (H\textsubscript{3}) by flexing the pad around
it.

Based on the above assumptions, we can come up with force-distance
curves to detach the beetle's leg via various pathways (Figure \ref{fig:Detachment-pathways}).
First, let us assume the hinge H\textsubscript{2} to be fixed, such
that both the distal and proximal pads can be combined to be a single
long pad with $N_{t}=60$ hairs. Path 1 shows the case where the pad
shows maximum possible adhesion. Here, the combined pad is vertically
pulled upwards while keeping the array perfectly parallel to the surface.
If the pad is detached by keeping H\textsubscript{1} fixed and maintaining
a tilt of $1\lyxmathsym{\textdegree}$ with the surface (path 2),
the forces dramatically reduces, with around 10 times reduction in
the adhesion compared to path 1. We can also detach the pad by switching
between the different mechanisms. Path 3 shows one such example, where,
initially the leg is pulled vertically up while keeping H\textsubscript{1}
fixed, stretching the hairs. On reaching point $a$, H\textsubscript{1}
is set free, which results in a sudden drop in force due to the excess
torque by the stretched hairs, tilting the array. Beyond this, the
force curve follows the free pull mechanism, with $\thicksim3.5$
times reduction in adhesion. An alternate strategy of switching between
mechanisms would be to first apply a load on the pad (path 4) and
compress the hairs until point $b$. Beyond this point, the claw can
be used as a hinge to detach the pad via flexing it around H\textsubscript{3},
which once again reduces the adhesion force. Now, if we assume the
hinge H\textsubscript{2} to be free such that two pads can behave
distinctly, we can consider the scenario where the proximal pad is
flexed around the distal pad at H\textsubscript{2} while keeping
H\textsubscript{1} fixed (path 5). After the proximal pad has completely
detached, H\textsubscript{1} can be freed up at point $c$ to detach
the distal pad via \emph{free pull} with very little force. This pathway
results in a $\thicksim5$ times reduction in adhesion.

\begin{figure}[H]
\includegraphics{Detachment_pathways}\caption{Force distance curves showing possible detachment pathways for a dock
beetle's leg, derived from the spring contact model. The curves are
offset laterally for clarity. Colours represent the distinct detachment
pathways, as labelled correspondingly, with arrows indicating the
direction of retraction. The different line style denotes the specific
detachment mechanism followed by any region of the pathway. The inset
schematic shows the assumed locations of the different hinges (H\protect\textsubscript{1},
H\protect\textsubscript{2} and H\protect\textsubscript{3}) employed
by the leg.\label{fig:Detachment-pathways}}
\end{figure}

The above analysis illustrates how the design of the beetle's hairy
adhesive pads is suitable for modulating its adhesion. Effective control
and release of its leg joints can help the insect to reduce the pad's
adhesion, allowing it to detach with little effort. High reduction
in adhesion is seen when the pad is tilted relative to the surface
during detachment, as a result of \emph{elastic weakening}. To the
best of our knowledge, there is no direct experimental evidence that
beetles can modulate its adhesion by taking advantage of this effect.
Considering that hair deformation occurs at length scales below 10
\textgreek{m}m, direct observation of this effect on running beetles
would be challenging. A recent study on PDMS micro-pillar arrays,
however, does indeed show a strong reduction in the adhesion force
due to slight misalignments with the surface\cite{RN252}. Based on
previously reported microscopic investigation of freely walking dock
beetles \cite{RN83}, we argue that the following experimental observations
provide support to our proposed theory: 1) The detachment was shown
to follow a three-dimensional twist of the leg, which suggests a complex
inhomogeneous deformation of hairs across the array, leading to \emph{elastic
weakening}. 2) The beetle can at times instantaneously detach all
its legs and ``drop'' itself while upside down. This could be explained
by the beetle freeing up its leg joints and using just its body weight
to provide the necessary force to detach all its legs via \emph{free
pull} (similar to path 3 above). 3) Only a fraction of the beetle's
pads made contact with the surface during locomotion, which indicates
that the pads should naturally be in a slightly tilted state. This
not only reduces the contact area, but also non-uniformly deforms
the hairs, both leading to a reduction in adhesion for easy detachment.
4) Contact images showed that the array ``peels'' from the proximal
to distal direction during detachment. However, the beetle's hairs
are attached to a relatively stiff backing\cite{RN53}, so it wouldn't
be able to ``peel'' its array, since peeling, strictly speaking,
depends on the elastic contribution of a thin flexible backing as
it bends during the process\cite{RN147}. Rather, the ``peeling''
observed in the beetle's case should be a result of the pad detaching
from the surface in a tilted orientation, causing the hairs to detach
in sequence. 5) The time scale of detachment was reported to be an
order of magnitude shorter than the attachment time scale, which could
be a result of the elastic recoil of the leg causing a spontaneous
propagation of the detachment front (Figure \ref{fig:Fixed-pull}).

There exists a limit to how much the pad can tilt, depending on its
geometry and material properties. Suppose the hair has a maximum linear
elastic strain limit, $\varepsilon_{m}$, and natural length, $l_{h,0}$.
Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
to its elastic limit, we can show from simple geometry, that, the
corresponding maximum limit in tilt angle is given by: 
\[
\theta_{limit}=\arctan\frac{l_{h,0}\varepsilon_{m}}{\left(N_{t}-1\right)w}
\]
$\theta_{limit}$ will limit the reduction factor for each of the
detachment mechanisms presented. Longer hairs can result in a lateral
collapse or bundling of hairs, imposing an additional constraint on
$\theta_{limit}$. Large deformation of hairs can also lead to buckling,
which will further limit the reduction in adhesion due to the smaller
effective modulus. Thus, the geometry of the individual hairs is also
crucial in effectively reducing adhesion by \emph{elastic weakening}.
Ideally, hairs with large diameters would be preferable to eliminate
buckling, and optimally long hairs would provide a large range of
angles to which the pad can be tilted while avoiding bundling.

\section{Conclusion}

Inhomogeneous deformation of hairs results in significant reductions
in the adhesion of a hairy pad system. Such a condition can be achieved
by either 1) pulling the pad while maintaining a constant tilt angle,
2) pulling the pad while maintaining a free leg joint or 3) flexing
the pad around the claw. Strategic control of the joint's mobility
can allow the leg to easily switch between the above mechanisms, thus
providing a simple way to reduce adhesion as per necessity. The presence
of a deformable leg can further trigger a spontaneous propagation
of hair detachment due to the leg's elastic recoil, making it suitable
for fast detachment. Arrays with low $\hat{f}_{p}$ and large number
of hairs, with a hair geometry that allows for large deformations
while avoiding buckling and lateral bundling represent the optimal
design conditions to maximize the range of control over adhesion.
The proposed theory is supported by previously reported experimental
observations of leg detachment in dock beetles and opens up new strategies
to achieve reversible adhesion in bio-inspired artificial adhesives
without the need of asymmetric structures.

\section{Acknowledgment}

We are grateful to Thomas Endlein, Ren\textcyr{\`\cyre} Hensel and
Bat-El Pinchasik for fruitful discussions. This work was funded by
\emph{Deutsche Forschungsgemeinschaft} (Grant number: PI 1351/2-1).

\appendix

\section{Appendix}

\subsection{Derivations}

\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}}

Suppose at a particular instant (Figure \ref{fig:Schematic}), there
are $n$ hairs in contact with the surface. The centre of the region
of the array in contact is at a vertical distance, $d'$, from the
surface. The net force on the whole array is,

\[
F_{net}=\stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)
\]

$l_{h,i}$ is the length of the $i^{th}$ hair, which is at a horizontal
distance, $x_{i}$, from the centre of the contact region. By simple
geometry, $l_{h,i}=d'-x_{i}\tan\theta$. Substituting $l_{h,i}$ in
above and noting that $\stackrel[i=1]{n}{\sum}x_{i}=0$ by symmetry,
we get:

\[
F_{net}=nk_{h}\left(d'-l_{h,0}\right)
\]

From geometry, $d_{s}$ and $d'$ is related as:

\[
\frac{d_{s}}{\sin\theta}-\frac{d'}{\sin\theta}=s-\frac{\left(n-1\right)w}{2}
\]

Substituting for $d'$, the net force, $F_{net}$, on the pad as a
function of distance, $d_{s}$, is:

\[
F_{net}=nk_{h}\left[d_{s}-l_{h,0}-\left[s-\frac{\left(n-1\right)w}{2}\right]\sin\theta\right]
\]

The above equation is valid for $d_{s}\leq d_{s,max}$ at a particular
value of $n$. We can get $d_{s,max}$ by considering the situation
just before the left most hair is about to detach (Figure \ref{fig:Schematic}).
This hair will be at its maximum length, $l_{h,p}$. Once again from
geometry, we see that $d_{s,max}$ and $l_{h,p}$ is related as:

\[
\frac{l_{h,p}}{\sin\theta}-\frac{d_{s,max}}{\sin\theta}=\left(n-1\right)w-s
\]

Substituting $l_{h,p}=\frac{f_{p}}{k_{h}}+l_{h,0}$ in above and simplifying,
we get:

\[
d_{s,max}=l_{h,0}+\frac{f_{p}}{k_{h}}+\left[s-\left(n-1\right)w\right]\sin\theta
\]

The net torque about the hinge due to the deformed hairs of the array
is,

\[
M_{net}=\stackrel[i=1]{n}{\sum}\lambda_{i}k_{h}\left(l_{h,i}-l_{h,0}\right)\cos\theta
\]

Here, $\lambda_{i}=s-\left(\frac{n-1}{2}w-\frac{x_{i}}{\cos\theta}\right)$
is the length of the lever arm between the $i^{th}$ hair and the
hinge.

Substituting for $l_{h,i}$ and eliminating $d'$ as before, we get:

\[
M_{net}=\stackrel[i=1]{n}{\sum}k_{h}\cos\theta\left[s-\left(\frac{n-1}{2}w-\frac{x_{i}}{\cos\theta}\right)\right]\left[d_{s}-\left(s-\frac{\left(n-1\right)w}{2}\right)\sin\theta-x_{i}\tan\theta-l_{h,0}\right]
\]

To calculate $\stackrel[i=1]{n}{\sum}x_{i}^{2}$, we follow:

\[
\stackrel[i=1]{n}{\sum}x_{i}^{2}=2\stackrel[i=1]{\frac{n}{2}}{\sum}x_{i}^{2}=2\stackrel[i=1]{\frac{n}{2}}{\sum}\left[w\cos\theta\left(i-\frac{1}{2}\right)^{2}\right]=2w^{2}\cos^{2}\theta\left[\stackrel[i=1]{\frac{n}{2}}{\sum}i^{2}-\stackrel[i=1]{\frac{n}{2}}{\sum}i-\stackrel[i=1]{\frac{n}{2}}{\sum}\frac{1}{4}\right]
\]

Using the identities $\stackrel[i=1]{N}{\sum}i^{2}=\frac{N\left(N+1\right)}{2}$
and $\stackrel[i=1]{N}{\sum}i^{2}=\frac{N\left(N+1\right)\left(2N+1\right)}{6}$
and simplifying, we get $\stackrel[i=1]{n}{\sum}x_{i}^{2}=n\left(\frac{n^{2}-1}{12}\right)w^{2}\cos^{2}\theta$.
This, together with $\stackrel[i=1]{n}{\sum}x_{i}=0$ (by symmetry),
the expression for $M_{net}$ above can be simplified to finally get:

\[
M_{net}=nk_{h}\cos\theta\left[\left(d_{s}-l_{h,0}\right)\left[s-\frac{\left(n-1\right)w}{2}\right]-\left\{ \left[s-\frac{\left(n-1\right)w}{2}\right]^{2}+\frac{n^{2}-1}{12}w^{2}\right\} \sin\theta\right]
\]

\bibliography{references}

\end{document}

### 2021-05-06 review/manuscript_HJB.tex

--- 2021-04-28 source/tex/manuscript.tex
@@
 at the end of their legs \cite{RN198,RN59}. These hairy adhesive
-pads help the animal to stay attached to any surface or detach easily
+pads help the animal to stay attached to 
+surfaces or detach easily
 at will for countless cycles, a property that is referred to as \emph{reversible
@@
 energy stored in the hair is dissipated, which increases W\textsubscript{adh}
-and thus adhesion is enhanced\cite{RN29,RN114}. Detachment of an
+and thus adhesion is enhanced\cite{RN29,RN114}. 
+% I do not understand the last sentence. What precisely does "`adhesion is enhanced"' mean? If the work of adhesion is fixed, how can it be adhanced? 
+Detachment of an
 individual hair can be explained based on Kendall's peeling theory\cite{RN147},
 which predicts low forces at high peeling angles.
+% The last sentence seems to belonmg more to the next paragraph.
 
-In the force balance approach, adhesion is characterized by pull-off
+In the force balance approach, adhesion is characterized by a pull-off
 force, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
@@
 
+% I suggest to describe both models a bit more in detail. What is a flaw sensitive regime? What does "`flaw"' mean and how is it related to adhesion?
+
 The theories presented so far suggests that low detachment force of
@@
 or curvature. However, some insects like male dock beetles predominantly
-possess flat ``mushroom'' tipped hairs on their pads\cite{RN19},
-which are relatively less asymmetric compared to the ``spatula''
+possess flat ``mushroom'' tipped hairs on their pads\cite{RN19}.
+They are relatively symmetric compared to the ``spatula''
 tipped hairs. This begs the question of how the beetle can still easily
@@
 
-In this work, we propose the possible mechanisms by which adhesive
-pads with symmetric hairs can be easily detached under a theoretical
-framework. The hairy pad is modelled as an array of springs and the
+In this work, we propose a mechanisms by which adhesive
+pads with symmetric hairs can easily detached from a surface. 
+The hairy pad is modeled as an array of springs and the
 force-balance approach is used to quantify the net adhesion \cite{RN117}.
@@
 process.
+% Is the angle at the hinge fixed? What happens, when I start pulling vertically?
 
@@
 Equation \ref{eq:force_n_d} will be valid for $d_{s}\leq d_{s,max}$. 
-
 The maximum possible adhesion of the array would be the case when
@@
 The net torque, $M_{net}$, about the hinge can be similarly derived
-(see Appendix):
+(Appendix):
 

### 2021-05-12 source/tex/manuscript.tex

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[british]{achemso}
+\documentclass[review]{elsarticle}
+
+\usepackage[unicode=true,colorlinks=false,hidelinks]{hyperref}
+\usepackage[pagewise]{lineno}
+\usepackage{float}
+\usepackage{url}
+
+\modulolinenumbers[5]
+
+\journal{Acta Biomaterialia}
 \usepackage[T2A,LGR,T1]{fontenc}
-\usepackage{babel}
+%\usepackage{babel}
 \usepackage{textcomp}
@@
 \usepackage{subscript}
-\usepackage[unicode=true,pdfusetitle,
- bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
- breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
- {hyperref}
+%\usepackage[unicode=true,pdfusetitle,
+% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+% breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
+% {hyperref}
 
+%
 \makeatletter
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-
-\title{Mechanisms of detachment in fibrillar adhesive systems}
-
-\author{Pranav Sudersan}
-
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
-
-\author{Hans-J\"{u}rgen Butt}
-
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
-
-\author{Michael Kappl}
-
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
-
-\email{kappl@mpip-mainz.mpg.de}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\SectionNumbersOn
+\makeatother
+
+%\SectionNumbersOn
 %\setkeys{acs}{doi = true}
@@
 \usepackage{subcaption}
-
-\makeatother
+\bibliographystyle{elsarticle-num}
 
 \begin{document}
+
+\begin{frontmatter}
+
+\title{Mechanisms of detachment in hairy adhesive systems}
+
+\author[mymainaddress]{Pranav Sudersan}
+
+\author[mymainaddress]{Michael Kappl\corref{mycorrespondingauthor}}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{kappl@mpip-mainz.mpg.de}
+
+\address[mymainaddress]{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
+Mainz, Germany}
+
 \begin{abstract}
@@
 The presented approaches can be potentially used to switch the adhesion
-state in bio-inspired artificial systems without the need of asymmetric
+state in bio-inspired artificial fibrillar adhesives without the need of asymmetric
 structures.
@@
 
+\begin{keyword}
+fibrillar adhesion \sep reversible adhesion \sep contact splitting \sep beetle \sep biomechanics 
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
+
 \section{Introduction}
 
-Over the past few decades, there has been numerous studies to understand
+Over the past few decades, there have been numerous studies to understand
 how animals such as geckos and insects are able to walk on surfaces
@@
 adhesion}. Previous attempts to theoretically explain adhesion in
-hairy pads\cite{RN40,RN120} has followed two fundamental approaches:
+hairy pads \cite{RN40,RN120} has followed two fundamental approaches:
 either by energy balance, or by force balance.
 
-In the energy balance approach, adhesion is characterized by ``work
-of adhesion'' (W\textsubscript{adh}) which is the energy required
+In the energy balance approach, adhesion is usually characterized by ``work
+of adhesion'' (W\textsubscript{adh}), which is the energy required
 to separate a pad from the surface. During detachment, the elastic
 energy stored in the hair is dissipated, which increases W\textsubscript{adh}
-and thus adhesion is enhanced\cite{RN29,RN114}. Detachment of an
-individual hair can be explained based on Kendall's peeling theory\cite{RN147},
+and thus adhesion is enhanced \cite{RN29,RN114}. Detachment of an
+individual hair can be explained based on Kendall's peeling theory \cite{RN147},
 which predicts low forces at high peeling angles.
@@
 which is the minimum force necessary to separate two surfaces from
-contact. Based on a ``cohesive zone model'', Hui et. al.\cite{RN72}
-had identified two regimes of single hair detachment: 1) a flaw sensitive
-regime, where contact failure occurs due to crack propagation leading
-to low \textgreek{sv}\textsubscript{p}, 2) a flaw insensitive regime,
-where the contact interface fails simultaneously, leading to high
+contact. Based on a ``cohesive zone model'', Hui et. al. \cite{RN72}
+had identified two regimes of single hair detachment: 1) a \emph{flaw sensitive}
+regime, where, for large hair raidus, contact failure occurs due to crack propagation, 
+initiated by a stress singularity at the edge of the hair, leading
+to low \textgreek{sv}\textsubscript{p}; 2) a \emph{flaw insensitive} regime,
+where, for small hair raidus, the contact interface fails simultaneously, leading to high
 \textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
@@
 to change adhesion by three orders of magnitude by laterally sliding
-and controlling the pulling angle to disorient the hairs. Federle\cite{RN20}
+and controlling the pulling angle to disorient the hairs. Federle \cite{RN20}
 had further argued that the curved shape of the hair helps the pad
@@
 or curvature. However, some insects like male dock beetles predominantly
-possess flat ``mushroom'' tipped hairs on their pads\cite{RN19},
+possess flat ``mushroom'' tipped hairs on their pads \cite{RN19},
 which are relatively less asymmetric compared to the ``spatula''
@@
 beetle have in fact demonstrated its superior adhesive strength in
-comparison to other geometries\cite{RN112,RN57}. Introducing asymmetry
+comparison to other geometries \cite{RN112,RN57}. Introducing asymmetry
 into the pillar geometry of such mimics for easy detachment is however
@@
 or by using special materials reacting to external stimuli such as
-magnetic field\cite{RN186}, UV light \cite{RN280} or temperature\cite{RN281}.
+magnetic field \cite{RN186}, UV light \cite{RN280} or temperature \cite{RN281}.
 
@@
 spaced apart by a width, $w$, and the array is of length, $L=\left(N_{t}-1\right)w$.
-The pad is oriented at an angle, $\theta$, while making contact with
+The pad is oriented at an instantaneous angle, $\theta$, while making contact with
 a flat smooth surface. Each hair can attain a maximum length, $l_{h,p}$,
@@
 
-Simplifying, we get (see Appendix section for derivation):
+Simplifying, we get (see Appendix for derivation):
 
@@
 during the process. We see that generally, the normal load, acting
-on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$.
+on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$ (Figure \ref{fig:Flex}).
 For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
@@
 weakening} can only reduce the array's adhesion force from $N_{t}$
-hairs down to a single hair.
+hairs down to a single hair at most.
 
@@
 two pads, with identical hairs of ``mushroom'' geometry. The distal
-and proximal pads possess roughly 500 and 1000 hairs, respectively\cite{RN19}.
+and proximal pads possess roughly 500 and 1000 hairs, respectively \cite{RN19}.
 Assuming the pads to be rectangular arrays of $20\times25$ and $40\times25$
@@
 hairs, respectively, by combining the hairs along the width. Based
-on reported measurements\cite{RN79}, the beetle's combined ``hair''
+on reported measurements \cite{RN79}, the beetle's ``combined hair''
 is thus considered to have an effective pull-off force, $f_{p}=0.5\times25=12.5$
-\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N/m
-. The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
+\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N m\protect\textsuperscript{-1}.
+The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
 long, spaced $w=10$ \textgreek{m}m apart. The adhesive pad also has
@@
 First, let us assume the hinge H\textsubscript{2} to be fixed, such
-that both the distal and proximal pads can be combined to be a single
+that both the distal and proximal pads are combined to be a single
 long pad with $N_{t}=60$ hairs. Path 1 shows the case where the pad
@@
 which once again reduces the adhesion force. Now, if we assume the
-hinge H\textsubscript{2} to be free such that two pads can behave
+hinge H\textsubscript{2} to be free such that the two pads can behave
 distinctly, we can consider the scenario where the proximal pad is
@@
 however, does indeed show a strong reduction in the adhesion force
-due to slight misalignments with the surface\cite{RN252}. Based on
+due to slight misalignments with the surface \cite{RN252}. Based on
 previously reported microscopic investigation of freely walking dock
@@
 to distal direction during detachment. However, the beetle's hairs
-are attached to a relatively stiff backing\cite{RN53}, so it wouldn't
+are attached to a relatively stiff backing \cite{RN53}, so it wouldn't
 be able to ``peel'' its array, since peeling, strictly speaking,
 depends on the elastic contribution of a thin flexible backing as
-it bends during the process\cite{RN147}. Rather, the ``peeling''
+it bends during the process \cite{RN147}. Rather, the ``peeling''
 observed in the beetle's case should be a result of the pad detaching
@@
 observations of leg detachment in dock beetles and opens up new strategies
-to achieve reversible adhesion in bio-inspired artificial adhesives
+to achieve reversible adhesion in bio-inspired artificial fibrillar adhesives
 without the need of asymmetric structures.
@@
 
-We are grateful to Thomas Endlein, Ren\textcyr{\`\cyre} Hensel and
-Bat-El Pinchasik for fruitful discussions. This work was funded by
-\emph{Deutsche Forschungsgemeinschaft} (Grant number: PI 1351/2-1).
+We are grateful to Hans-J\"{u}rgen Butt and Thomas Endlein for reviewing the text, and thank Ren\textcyr{\`\cyre} Hensel and
+Bat-El Pinchasik for fruitful discussions. This work was supported by the Deutsche Forschungsgemeinschaft
+[Grant number: PI 1351/2-1] and the Max Planck Graduate Center with the Johannes Gutenberg-Universit\"{a}t Mainz [MPGC].
 
@@
 
-\section{Appendix}
+\section{{Derivations}}
 
-\subsection{Derivations}
+%\subsection{Derivations}
 

### 2021-06-03 source/tex/manuscript.tex
Final edits: "fibrillar", new references added

@@
 
-\title{Mechanisms of detachment in hairy adhesive systems}
+\title{Mechanisms of detachment in fibrillar adhesive systems}
 
@@
 to effortless detachment of the leg is enabled by the asymmetric geometry
-of the hairs. In this study, we propose possible mechanisms by which
-a hairy pad can be easily detached even when the hairs possess no
-asymmetry. Based on a spring-based model, we consider three modes
+of the hairs. In this study, we propose mechanisms by which
+a hairy pad can be easily detached, even when the hairs possess no
+asymmetry. Here, we examine the possible function of the leg joint and the claws.
+Based on a spring-based model, we consider three modes
 of detachment: vertically pulling the pad while maintaining either
@@
 across the array, an effect that we call ``\emph{elastic weakening}''.
-Our proposed model illustrates the design advantage provided by hairy
+Our proposed model illustrates the design advantage provided by such fibrillar
 adhesive systems, which not only provides strong adhesion, but also
@@
 The presented approaches can be potentially used to switch the adhesion
-state in bio-inspired artificial fibrillar adhesives without the need of asymmetric
-structures.
+state in bio-inspired fibrillar adhesives, by incorporating artificial joints and claws into their design, 
+without the need of asymmetric or stimuli-responsive fibrillar structures.
 \end{abstract}
@@
 of any direction while defying gravity. A microscopic observation
-reveals that, in many cases, animals have a dense array of hairy structures
-at the end of their legs \cite{RN198,RN59}. These hairy adhesive
+reveals that, in many cases, animals have a dense array of fibrillar structures
+at the end of their legs \cite{RN198,RN59}. These "hairy" adhesive
 pads help the animal to stay attached to any surface or detach easily
@@
 and thus adhesion is enhanced \cite{RN29,RN114}. Detachment of an
-individual hair can be explained based on Kendall's peeling theory \cite{RN147},
+individual hair can be explained based on Kendall's peeling theory \cite{RN147, RN296},
 which predicts low forces at high peeling angles.
@@
 The theories presented so far suggests that low detachment force of
-a hairy pad can be attained by 1) increasing the stress concentration
+a fibrillar adhesive pad can be attained by 1) increasing the stress concentration
 by peeling the pad at high angles, or 2) laterally shearing the pad
@@
 framework. The hairy pad is modelled as an array of springs and the
-force-balance approach is used to quantify the net adhesion \cite{RN117}.
+force-balance approach is used to quantify the net adhesion \cite{RN117, RN253}.
 We hope our work to provide strategies to control the adhesion force
@@
 
-The hairy pad is assumed to be a one dimensional array of $N_{t}$
+The fibrillar adhesive pad is assumed to be a one dimensional array of $N_{t}$
 hairs, each behaving like a spring with spring constant, $k_{h}$,
@@
 \begin{figure}[H]
-\includegraphics{Figure1-model_schematic}\caption{Spring contact model of a hairy adhesive pad. The pad consists of
+\includegraphics{Figure1-model_schematic}\caption{Spring contact model of a fibrillar adhesive pad. The pad consists of
 an array of $N_{t}$ hairs connected to a deformable leg at the hinge.
@@
 \begin{figure}[H]
-\includegraphics{Case1-Fixed_pull}\caption{Force distance curves for a hairy pad, pulled vertically upwards with
+\includegraphics{Case1-Fixed_pull}\caption{Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
 a fixed hinge between the pad and the leg (\emph{Fixed pull}). The
@@
 
-The hairy adhesive pad can be detached by pulling it vertically upwards
+The fibrillar adhesive pad can be detached by pulling it vertically upwards
 while maintaining a constant tilt angle, $\theta$, with the surface.
@@
 hair, resulting in a spontaneous propagation of the detachment front
-until the pad completely breaks contact with the surface.
+until the pad completely breaks contact with the surface. This is consistent with 
+a recent report of catastrophic failure, due to a similar recoil effect of the measurement system,
+seen in micro-fibrillar adhesives with a narrow variance of individual fibril adhesive strengths \cite{RN273}.
 
@@
 
-\includegraphics{Case2-Free_pull}\caption{Force distance curves for a hairy pad, pulled vertically upwards with
+\includegraphics{Case2-Free_pull}\caption{Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
 a free hinge between the pad and the leg (\emph{Free pull}). $s$
@@
 \begin{figure}[H]
-\includegraphics{Case3-Fixed_flex}\caption{Force curves for a hairy pad detached by flexing it about the claw.
+\includegraphics{Case3-Fixed_flex}\caption{Force curves for a fibrillar adhesive pad detached by flexing it about the claw.
 $\hat{F}_{pull}=\frac{F_{pull}}{k_{h}w}$ is the normalised pulling
@@
 Based on the three modes of detachment discussed in the previous sections,
-one can think of several strategies to detach a hairy adhesive pad
+one can think of several strategies to detach a fibrillar adhesive pad
 from the surface. To illustrate this, let us consider the adhesive
@@
 Inhomogeneous deformation of hairs results in significant reductions
-in the adhesion of a hairy pad system. Such a condition can be achieved
+in the adhesion of a fibrillar system. Such a condition can be achieved
 by either 1) pulling the pad while maintaining a constant tilt angle,
 2) pulling the pad while maintaining a free leg joint or 3) flexing
-the pad around the claw. Strategic control of the joint's mobility
+the pad around the claw. Strategic control of the joint's mobility or claw
 can allow the leg to easily switch between the above mechanisms, thus
@@
 The proposed theory is supported by previously reported experimental
-observations of leg detachment in dock beetles and opens up new strategies
-to achieve reversible adhesion in bio-inspired artificial fibrillar adhesives
-without the need of asymmetric structures.
+observations of leg detachment in dock beetles and highlights possible role of the leg joint and claws to 
+enable reversible adhesion. Similar strategies could potentially be adopted in the design of bio-inspired 
+artificial fibrillar adhesives to easily switch the adhesion state without the need of asymmetric structures.
 
@@
 
-We are grateful to Hans-J\"{u}rgen Butt and Thomas Endlein for reviewing the text, and thank Ren\textcyr{\`\cyre} Hensel and
-Bat-El Pinchasik for fruitful discussions. This work was supported by the Deutsche Forschungsgemeinschaft
+We are grateful to Prof. Dr. Hans-J\"{u}rgen Butt and Dr. Thomas Endlein (Max Planck Institute for Polymer Research, Germany) for reviewing the text, and thank Dr. Ren\textcyr{\`\cyre} Hensel
+(Leibniz Institute for New Materials, Germany) and
+Dr. Bat-El Pinchasik (Tel-Aviv University, Israel) for fruitful discussions. This work was supported by the Deutsche Forschungsgemeinschaft
 [Grant number: PI 1351/2-1] and the Max Planck Graduate Center with the Johannes Gutenberg-Universit\"{a}t Mainz [MPGC].

### 2021-06-09 source/tex/manuscript.tex
finalized MS for submission to acta
fixed references format
fixed hinge/joint phrase
included statement of significance

@@
 \author[mymainaddress]{Michael Kappl\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
+\cortext[mycorrespondingauthor]{Corresponding author. \emph{Telephone:} +49 6131 379-114}
 \ead{kappl@mpip-mainz.mpg.de}
@@
 
+\section*{Statement of Significance}
+Insects such as flies or beetles have the ability to walk on any surface against gravity. It was previously shown that
+these insects possess a dense array of micrometer sized hairs on their legs. These hairy legs are responsible for the 
+insect's strong adhesion to surfaces by resisting contact failure due to micro-roughness or defects on the surface.
+In this work, we theoretically show that, a hairy design of the leg not only provides strong adhesion, but can also allow easy detachment from a surface.
+This is achieved simply by modulating the leg's tilt relative to the surface with the aid of its leg joint or claws.
+Such a design can thus inspire artificial adhesives with switchable adhesion properties.
+
 \section{Introduction}
@@
 individual hair can be explained based on Kendall's peeling theory \cite{RN147, RN296},
-which predicts low forces at high peeling angles.
+which predicts low adhesion at high peeling angles.
 
@@
 had identified two regimes of single hair detachment: 1) a \emph{flaw sensitive}
-regime, where, for large hair raidus, contact failure occurs due to crack propagation, 
+regime, where, for large hair radius, contact failure occurs due to crack propagation, 
 initiated by a stress singularity at the edge of the hair, leading
 to low \textgreek{sv}\textsubscript{p}; 2) a \emph{flaw insensitive} regime,
-where, for small hair raidus, the contact interface fails simultaneously, leading to high
+where, for small hair radius, the contact interface fails simultaneously, leading to high
 \textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
@@
 $k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
-array at a distance, $s$, from the right end of the array. The hinge
+array at a distance, $s$, from the right end of the array. The hinge (or joint) 
 is at a vertical distance, $d_{s}$, from the surface. The hairs are
@@
 $F_{net}$ is the net force on the pad and $M_{net}$ is the the net
-torque about the hinge, at a particular instant during the detachment
+torque about the joint, at a particular instant during the detachment
 process.
@@
 \begin{figure}[H]
-\includegraphics{Figure1-model_schematic}\caption{Spring contact model of a fibrillar adhesive pad. The pad consists of
-an array of $N_{t}$ hairs connected to a deformable leg at the hinge.
+\includegraphics{Figure1-model_schematic}\caption{\textbf{Spring contact model of a fibrillar adhesive pad.} The pad consists of
+an array of $N_{t}$ hairs connected to a deformable leg at the joint.
 At a particular distance, $d_{s}$, $n$ number of hairs are in contact
@@
 
-Simplifying, we get (see Appendix for derivation):
+Simplifying, we get (see Appendix A for derivation):
 
@@
 
-The net torque, $M_{net}$, about the hinge can be similarly derived
-(see Appendix):
+The net torque, $M_{net}$, about the joint can be similarly derived
+(see Appendix A):
 
@@
 
-Let us now consider the scenario where even the leg above the hinge
+Let us now consider the scenario where even the leg above the joint
 can undergo elastic stretching together with the hairs. When a hair
@@
 a surface: 1) \emph{Fixed pull}, where the pad is pulled vertically
-up while keeping a fixed leg-hinge, 2) \emph{Free pull,} where the
-pad is pulled vertically up while keeping the leg-hinge free to allow
-rotation of the array and 3) \emph{Flex}, where the pad is hinged
+up while keeping a fixed leg joint; 2) \emph{Free pull,} where the
+pad is pulled vertically up while keeping the leg joint free to allow
+rotation of the array; 3) \emph{Flex}, where the pad is hinged
 to an external point (claw-hinge), and detached in a rotary fashion,
@@
 \begin{figure}[H]
-\includegraphics{Case1-Fixed_pull}\caption{Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a fixed hinge between the pad and the leg (\emph{Fixed pull}). The
+\includegraphics{Case1-Fixed_pull}\caption{\textbf{Detachment by fixed pull.} 
+Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
+a fixed joint between the pad and the leg (\emph{Fixed pull}). The
 tilt angle, $\theta$, of the array is kept fixed during detachment.
@@
 while maintaining a constant tilt angle, $\theta$, with the surface.
-This can be achieved if the joint connecting the leg to the array
-(leg-hinge) is kept fixed. Equations \ref{eq:force_n_d}, \ref{eq:d_max}
+This can be achieved if the joint connecting the leg to the array is kept fixed. 
+Equations \ref{eq:force_n_d}, \ref{eq:d_max}
 and \ref{eq:simul_detach} can be used to get the resulting force-distance
@@
 
-\includegraphics{Case2-Free_pull}\caption{Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a free hinge between the pad and the leg (\emph{Free pull}). $s$
-is the distance between the leg-hinge and the right end of the array
-and $L$ is the array length. The free hinge allows further tilting
+\includegraphics{Case2-Free_pull}\caption{\textbf{Detachment by free pull.} 
+Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
+a free joint between the pad and the leg (\emph{Free pull}). $s$
+is the distance between the leg joint and the right end of the array
+and $L$ is the array length. The free joint allows further tilting
 of the array during the vertical pull. The leg is either stiff ($k_{l}\rightarrow\infty$)
@@
 where the adhesive pad is pulled vertically upwards for detachment.
-However now, the leg-hinge is assumed to be free. In this case, the
+However now, the leg joint is assumed to be free. In this case, the
 array will reorient itself to maintain a zero net torque about the
-leg-hinge during the entire detachment process. At any given instant,
+joint during the entire detachment process. At any given instant,
 the tilt angle, $\theta$, can be found by setting $M_{net}$ to zero
@@
 curves during a free vertical pull of the adhesive pad. Since the
-position of the leg-hinge will influence the net torque, we use the
+position of the leg joint will influence the net torque, we use the
 ratio, $s/L$, to study its effect on the detachment forces.
 
-Maximum adhesion is seen when the leg-hinge is positioned at the centre
+Maximum adhesion is seen when the leg joint is positioned at the centre
 of the array, i.e. $s/L=0.5$ (Figure \ref{fig:Free-pull}). Here,
@@
 remains parallel to the substrate until all hairs detach simultaneously
-at $\hat{d_{s}}=0.1$. Shifting the position of the leg-hinge further
+at $\hat{d_{s}}=0.1$. Shifting the position of the joint further
 away from the array centre leads to lower forces or adhesion. The
@@
 \begin{figure}[H]
-\includegraphics{Case3-Fixed_flex}\caption{Force curves for a fibrillar adhesive pad detached by flexing it about the claw.
+\includegraphics{Case3-Fixed_flex}\caption{\textbf{Detachment by flex.}
+Force curves for a fibrillar adhesive pad detached by flexing it about the claw.
 $\hat{F}_{pull}=\frac{F_{pull}}{k_{h}w}$ is the normalised pulling
@@
 Let $s_{h}$ be the distance between the claw-hinge and the right
-end of the array; $s_{l}$ be the distance between the fixed leg-hinge
+end of the array; $s_{l}$ be the distance between the fixed leg joint
 and the right end of the array. To illustrate the mechanism, let us
@@
 $\hat{f}_{p}$ influences the reduction factor under each mode of
-detachment (Figure \ref{fig:Reduction-factor_fp}). From the heat
-maps, one can generally say that lower values of $\hat{f}_{p}$ increase
+detachment (Figure \ref{fig:Reduction-factor_fp}). From the colour plots, 
+one can generally say that lower values of $\hat{f}_{p}$ increase
 the reduction factor and thus provide a greater possibility of controlling
@@
 \begin{figure}[H]
-\noindent \includegraphics{Reduction_factor-fp}\caption{Heat maps showing the effect of the dimensionless parameter, $\hat{f}_{p}$,
+\noindent \includegraphics{Reduction_factor-fp}\caption{\textbf{Effect of $\hat{f}_{p}$ on reduction factor.}
+Colour plots showing the effect of the dimensionless parameter, $\hat{f}_{p}$,
 on the reduction factor for each mode of detachment. Here, we fix
@@
 no influence on the reduction factor. On the other hand, shifting
-the position of the leg-hinge further away from the array (i.e. high
+the position of the leg joint further away from the array (i.e. high
 $s/L$) results in large values of $r$. In this scenario, the higher
@@
 the number of hairs, $N_{t}$, on the reduction factor (Figure \ref{fig:Reduction-factor-Nt}).
-The heat maps show that high $N_{t}$ increases $r$ irrespective
+The colour plots show that high $N_{t}$ increases $r$ irrespective
 of the mode of detachment. Under a tilted state, more number of hairs
@@
 \noindent \begin{centering}
-\includegraphics{Reduction_factor-Nt}\caption{Heat maps showing the effect of the number of hairs, $N_{t}$, on
+\includegraphics{Reduction_factor-Nt}\caption{\textbf{Effect of $N_{t}$ on reduction factor.} 
+Colour plots showing the effect of the number of hairs, $N_{t}$, on
 the reduction factor for each mode of detachment. Here, we fix the
@@
 curves to detach the beetle's leg via various pathways (Figure \ref{fig:Detachment-pathways}).
-First, let us assume the hinge H\textsubscript{2} to be fixed, such
-that both the distal and proximal pads are combined to be a single
+First, let us assume the joint H\textsubscript{2} to be fixed, such
+that both the distal and proximal pads can be combined to behave like a single
 long pad with $N_{t}=60$ hairs. Path 1 shows the case where the pad
@@
 pulled upwards while keeping the array perfectly parallel to the surface.
-If the pad is detached by keeping H\textsubscript{1} fixed and maintaining
+If this combined pad is detached by keeping H\textsubscript{1} fixed and maintaining
 a tilt of $1\lyxmathsym{\textdegree}$ with the surface (path 2),
@@
 torque by the stretched hairs, tilting the array. Beyond this, the
-force curve follows the free pull mechanism, with $\thicksim3.5$
+force curve follows the \emph{free pull} mechanism, with $\thicksim3.5$
 times reduction in adhesion. An alternate strategy of switching between
@@
 which once again reduces the adhesion force. Now, if we assume the
-hinge H\textsubscript{2} to be free such that the two pads can behave
+joint H\textsubscript{2} to be free such that the two pads can behave
 distinctly, we can consider the scenario where the proximal pad is
@@
 \begin{figure}[H]
-\includegraphics{Detachment_pathways}\caption{Force distance curves showing possible detachment pathways for a dock
+\includegraphics{Detachment_pathways}\caption{\textbf{Beetle leg detachment pathways.}
+Force distance curves showing possible detachment pathways for a dock
 beetle's leg, derived from the spring contact model. The curves are
@@
 inhomogeneous deformation of hairs across the array, leading to \emph{elastic
-weakening}. 2) The beetle can at times instantaneously detach all
+weakening}, which is suited for easy detachment. 2) The beetle can at times instantaneously detach all
 its legs and ``drop'' itself while upside down. This could be explained
@@
 observed in the beetle's case should be a result of the pad detaching
-from the surface in a tilted orientation, causing the hairs to detach
+from the surface in a tilted orientation, causing the hairs to distinctly detach
 in sequence. 5) The time scale of detachment was reported to be an
@@
 Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
-to its elastic limit, we can show from simple geometry, that, the
+to its elastic limit, one can derive from simple geometry, that, the
 corresponding maximum limit in tilt angle is given by: 
@@
 
-The net torque about the hinge due to the deformed hairs of the array
+The net torque about the joint due to the deformed hairs of the array
 is,
@@
 is the length of the lever arm between the $i^{th}$ hair and the
-hinge.
+joint.
 

### 2021-06-09 source/tex/manuscript.tex
added statement of significance and declaration interests

@@
 \linenumbers
-
-\section*{Statement of Significance}
-Insects such as flies or beetles have the ability to walk on any surface against gravity. It was previously shown that
-these insects possess a dense array of micrometer sized hairs on their legs. These hairy legs are responsible for the 
-insect's strong adhesion to surfaces by resisting contact failure due to micro-roughness or defects on the surface.
-In this work, we theoretically show that, a hairy design of the leg not only provides strong adhesion, but can also allow easy detachment from a surface.
-This is achieved simply by modulating the leg's tilt relative to the surface with the aid of its leg joint or claws.
-Such a design can thus inspire artificial adhesives with switchable adhesion properties.
 

### 2021-08-10 source/tex/manuscript.tex
abstract shortened, line numbers removed for RSIF submission.

@@
 
-\modulolinenumbers[5]
+%\modulolinenumbers[5]
 
@@
 reduced due to elastic forces when the hairs deform non-uniformly
-across the array, an effect that we call ``\emph{elastic weakening}''.
+across the array. %, an effect that we call ``\emph{elastic weakening}''.
 Our proposed model illustrates the design advantage provided by such fibrillar
@@
 
-\linenumbers
+%\linenumbers
 

### 2022-04-29 source/tex/manuscript.tex
zip file of tex files
line numbers added
small corrections in terms based on comments

@@
 to effortless detachment of the leg is enabled by the asymmetric geometry
-of the hairs. In this study, we propose mechanisms by which
+of the tarsal hairs. In this study, we propose mechanisms by which
 a hairy pad can be easily detached, even when the hairs possess no
-asymmetry. Here, we examine the possible function of the leg joint and the claws.
+asymmetry. Here, we examine the possible function of the tibia-tarsus (t-t) leg joint and the claws.
 Based on a spring-based model, we consider three modes
 of detachment: vertically pulling the pad while maintaining either
-a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
+a 1) fixed or a 2) free t-t leg joint, or by 3) flexing the pad about
 the claw. We show that in all cases, the adhesion force can be significantly
@@
 
-%\linenumbers
+\linenumbers
 
@@
 force-balance approach is used to quantify the net adhesion \cite{RN117, RN253}.
+Here, we focus our analysis to only normal adhesion force necessary to separate 
+the pad from a flat surface.
 We hope our work to provide strategies to control the adhesion force
@@
 $k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
-array at a distance, $s$, from the right end of the array. The hinge (or joint) 
+array at a distance, $s$, from the right end of the array. The hinge, analogous to the tarsus-tibia (t-t) leg joint of an insect, 
 is at a vertical distance, $d_{s}$, from the surface. The hairs are
@@
 $F_{net}$ is the net force on the pad and $M_{net}$ is the the net
-torque about the joint, at a particular instant during the detachment
-process.
+moment about the hinge, at a particular instant during the detachment
+process. The contact points between the hair and the surface is assumed to be laterally fixed due to high friction forces.
 
@@
 \includegraphics{Figure1-model_schematic}\caption{\textbf{Spring contact model of a fibrillar adhesive pad.} The pad consists of
-an array of $N_{t}$ hairs connected to a deformable leg at the joint.
+an array of $N_{t}$ hairs connected to a deformable leg at the hinge.
 At a particular distance, $d_{s}$, $n$ number of hairs are in contact
@@
 
-The net torque, $M_{net}$, about the joint can be similarly derived
+The net moment, $M_{net}$, about the joint can be similarly derived
 (see Appendix A):
@@
 a surface: 1) \emph{Fixed pull}, where the pad is pulled vertically
-up while keeping a fixed leg joint; 2) \emph{Free pull,} where the
-pad is pulled vertically up while keeping the leg joint free to allow
+up while keeping a fixed hinge (t-t leg joint); 2) \emph{Free pull,} where the
+pad is pulled vertically up while keeping the hinge (t-t leg joint) free to allow
 rotation of the array; 3) \emph{Flex}, where the pad is hinged
@@
 emulating the claw function in insects. To investigate each case in
-detail, let us assume a pad with $N_{t}=25$ hairs and $\hat{f_{p}}=0.1$
-attached to a stiff leg ($k_{l}\rightarrow\infty$). The situation
-of a soft leg ($k_{l}/k_{h}=10$) is also considered for the first
+detail, let us assume a pad to be a one dimensional analogue of a 
+dock beetle's adhesive pad \cite{RN19, RN79} with $N_{t}=25$ hairs and $\hat{f_{p}}=0.1$
+attached to a stiff leg (tibia) with $k_{l}\rightarrow\infty$. The situation
+of a soft leg (tibia) with $k_{l}/k_{h}=10$ is also considered for the first
 two cases involving vertical detachment.
@@
 \begin{figure}[H]
-\includegraphics{Case1-Fixed_pull}\caption{\textbf{Detachment by fixed pull.} 
+\includegraphics{Case1-Fixed_pull}\caption{\textbf{Detachment by \emph{Fixed Pull}.} 
 Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a fixed joint between the pad and the leg (\emph{Fixed pull}). The
+a fixed hinge (tarsus-tibia leg joint). The
 tilt angle, $\theta$, of the array is kept fixed during detachment.
-The leg is either stiff ($k_{l}\rightarrow\infty$) or soft ($k_{l}/k_{h}=10$).
+The leg (tibia) is either stiff ($k_{l}\rightarrow\infty$) or soft ($k_{l}/k_{h}=10$).
 Positive force values represent attraction. The green dashed line
@@
 while maintaining a constant tilt angle, $\theta$, with the surface.
-This can be achieved if the joint connecting the leg to the array is kept fixed. 
+This can be achieved if the hinge (t-t leg joint) is kept fixed. 
 Equations \ref{eq:force_n_d}, \ref{eq:d_max}
@@
 
-For the case of a stiff leg, we see that at small distances, all hairs
+For the case of a stiff leg (tibia), we see that at small distances, all hairs
 of the pad are in contact with the surface, resulting in a linear
@@
 
-For the case of a soft leg, we observe a similar effect of tilt angle
+For the case of a soft leg (tibia), we observe a similar effect of tilt angle
 on the force curves as before. The maximum adhesion force at a particular
@@
 
-\includegraphics{Case2-Free_pull}\caption{\textbf{Detachment by free pull.} 
+\includegraphics{Case2-Free_pull}\caption{\textbf{Detachment by \emph{Free Pull}.} 
 Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a free joint between the pad and the leg (\emph{Free pull}). $s$
+a free hinge (tarsus-tibia leg joint). $s$
 is the distance between the leg joint and the right end of the array
 and $L$ is the array length. The free joint allows further tilting
-of the array during the vertical pull. The leg is either stiff ($k_{l}\rightarrow\infty$)
+of the array during the vertical pull. The leg (tibia) is either stiff ($k_{l}\rightarrow\infty$)
 or soft ($k_{l}/k_{h}=10$). Positive force values represent attraction.

### 2022-08-13 source/tex/manuscript.tex

@@
 
-\journal{Acta Biomaterialia}
+\journal{Journal of Theoretical Biology}
 \usepackage[T2A,LGR,T1]{fontenc}
@@
 of the tarsal hairs. In this study, we propose mechanisms by which
-a hairy pad can be easily detached, even when the hairs possess no
-asymmetry. Here, we examine the possible function of the tibia-tarsus (t-t) leg joint and the claws.
-Based on a spring-based model, we consider three modes
+the hairy pad can be easily detached, even when the hairs possess no
+asymmetry. Here, we examine the possible function of the tibia-tarsus leg joint and the claws. Based on a spring-based model, we consider three modes
 of detachment: vertically pulling the pad while maintaining either
-a 1) fixed or a 2) free t-t leg joint, or by 3) flexing the pad about
+a 1) fixed or a 2) free joint, or by 3) flexing the pad about
 the claw. We show that in all cases, the adhesion force can be significantly
@@
 across the array. %, an effect that we call ``\emph{elastic weakening}''.
-Our proposed model illustrates the design advantage provided by such fibrillar
-adhesive systems, which not only provides strong adhesion, but also
-allows easy detachment, making it suitable as organs for fast locomotion.
+Our proposed model illustrates the design advantage of such fibrillar
+adhesive systems, that not only provide strong adhesion, but also
+allow easy detachment, making them suitable as organs for fast locomotion and reliable hold.
 The presented approaches can be potentially used to switch the adhesion
-state in bio-inspired fibrillar adhesives, by incorporating artificial joints and claws into their design, 
-without the need of asymmetric or stimuli-responsive fibrillar structures.
+state in bio-inspired fibrillar adhesives, by incorporating artificial joints and claws into their design, without the need of asymmetric or stimuli-responsive fibrillar structures.
 \end{abstract}
@@
 Over the past few decades, there have been numerous studies to understand
-how animals such as geckos and insects are able to walk on surfaces
-of any direction while defying gravity. A microscopic observation
+how animals, such as geckos and insects, are able to walk on surfaces
+of any direction while seemingly defying gravity. A microscopic observation
 reveals that, in many cases, animals have a dense array of fibrillar structures
-at the end of their legs \cite{RN198,RN59}. These "hairy" adhesive
+at the end of their legs \cite{RN198,RN59}. These \emph{hairy} adhesive
 pads help the animal to stay attached to any surface or detach easily
@@
 adhesion}. Previous attempts to theoretically explain adhesion in
-hairy pads \cite{RN40,RN120} has followed two fundamental approaches:
-either by energy balance, or by force balance.
+hairy pads \cite{RN40,RN120,Popov2016BiologicalMW} has followed two fundamental approaches: either by energy balance, or by force balance.
 
-In the energy balance approach, adhesion is usually characterized by ``work
-of adhesion'' (W\textsubscript{adh}), which is the energy required
+In the energy balance approach, adhesion is usually characterized by \emph{work
+of adhesion} (W\textsubscript{adh}), which is the energy required
 to separate a pad from the surface. During detachment, the elastic
-energy stored in the hair is dissipated, which increases W\textsubscript{adh}
+energy stored in the hair is dissipated, that increases W\textsubscript{adh}
 and thus adhesion is enhanced \cite{RN29,RN114}. Detachment of an
@@
 
-In the force balance approach, adhesion is characterized by pull-off
-force, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
+In the force balance approach, adhesion is characterized by \emph{pull-off
+force}, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
 which is the minimum force necessary to separate two surfaces from
-contact. Based on a ``cohesive zone model'', Hui et. al. \cite{RN72}
-had identified two regimes of single hair detachment: 1) a \emph{flaw sensitive}
+contact. Based on a \emph{cohesive zone model}, Hui et. al. \cite{RN72}
+have identified two regimes of single hair detachment: 1) a \emph{flaw sensitive}
 regime, where, for large hair radius, contact failure occurs due to crack propagation, 
@@
 where, for small hair radius, the contact interface fails simultaneously, leading to high
-\textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
-that the ``spatula'' shaped hair tips in a gecko's toe allows it
+\textgreek{sv}\textsubscript{p}. Likewise, Tian et. al. \cite{RN230} have shown
+that the spatula-shaped hair tips in a gecko's toe allows it
 to change adhesion by three orders of magnitude by laterally sliding
-and controlling the pulling angle to disorient the hairs. Federle \cite{RN20}
-had further argued that the curved shape of the hair helps the pad
-to stay attached when pulled proximally, and easily detached by elastic
+and controlling the pulling angle to disorient the hairs. The detailed mechanics of the
+spatula-shaped hair design for controlling adhesion have been extensively studied by theoretical modelling \cite{pantano2011, sauer2013, Wu2015, kligerman2020, Grill2021, Gouravaraju2021}, artificial mimics \cite{RN57, Murphy2007, Menguc2012, Chary2013, Kim2017} as well as in several biological systems \cite{autumn2000,Langer2004,Varenberg2010}.
+Federle \cite{RN20}
+has further argued that the curved shape of the hair helps the pad
+to stay attached when pulled proximally and easily detached by elastic
 recoil when pushed distally.
 
-The theories presented so far suggests that low detachment force of
-a fibrillar adhesive pad can be attained by 1) increasing the stress concentration
-by peeling the pad at high angles, or 2) laterally shearing the pad
+The theory presented so far suggests that a low detachment force of
+a fibrillar adhesive pad can be achieved either by increasing the stress concentration
+by peeling the pad at high angles, or by laterally shearing the pad
 before pull-off, which requires the hairs to have an asymmetric geometry
 or curvature. However, some insects like male dock beetles predominantly
-possess flat ``mushroom'' tipped hairs on their pads \cite{RN19},
-which are relatively less asymmetric compared to the ``spatula''
-tipped hairs. This begs the question of how the beetle can still easily
-detach their legs during locomotion, since these mushroom shaped hairs
-should be resilient to detachment via lateral shearing. Artificial
-micro-pillar adhesives mimicking the mushroom shaped hairs of the
-beetle have in fact demonstrated its superior adhesive strength in
-comparison to other geometries \cite{RN112,RN57}. Introducing asymmetry
-into the pillar geometry of such mimics for easy detachment is however
-challenging due to current limitations in fabrication techniques and
-difficulty in scaling-up for practical applications \cite{RN57}.
+possess mushroom-shaped hairs with flat discoid terminals on their pads \cite{RN19},
+that are relatively less asymmetric compared to the spatula-shaped hairs. These mushroom-shaped hairs have in fact been shown to possess superior
+adhesion compared to the spatula-shaped hairs \cite{RN112,RN57} and are generally resistant to detachment via lateral shear \cite{Heepe2014}.
+Yet, how does the beetles possessing such mushroom-shaped hairs still easily detach their legs during locomotion?
+Besides, from an application perspective, introducing asymmetry
+into the pillar geometry to construct spatula-shaped artificial biomimetic 
+adhesives for easy detachment is challenging due to current limitations in fabrication techniques and difficulty in scaling-up \cite{RN57}.
 Alternate strategies are thus desired to switch the adhesion state
-of symmetric pillar arrays in a reversible manner, e.g. by buckling
+of symmetric pillar arrays in a reversible manner. This can be achieved, for example, by buckling
 the pillars under compressive load leading to their contact loss \cite{RN279}
@@
 
-In this work, we propose the possible mechanisms by which adhesive
-pads with symmetric hairs can be easily detached under a theoretical
-framework. The hairy pad is modelled as an array of springs and the
-force-balance approach is used to quantify the net adhesion \cite{RN117, RN253}.
-Here, we focus our analysis to only normal adhesion force necessary to separate 
-the pad from a flat surface.
-We hope our work to provide strategies to control the adhesion force
-of an artificial micro-pillar adhesive, which has applications in
+Employing the force-balance approach, in this work we theoretically model the possible mechanisms by which adhesive pads with axially-symmetric hairs can be easily detached, without the need of any spatula-like asymmetry.
+Here, we focus our analysis on normal adhesion force necessary to separate 
+the pad from a flat surface under a purely mechanical action.
+We found that the maximum force necessary to detach the leg can be significantly reduced by strategically controlling the tilt, joints and claws of the adhesive system.
+We hope our work to provide new approaches to control the adhesion force
+of an artificial micro-pillar adhesive, that has applications in
 bio-inspired climbing robots, pick-and-place operations and reusable
@@
 
-The fibrillar adhesive pad is assumed to be a one dimensional array of $N_{t}$
+Similar to previous approaches \cite{RN117, RN253}, the fibrillar adhesive pad is assumed to be a one-dimensional array of $N_{t}$
 hairs, each behaving like a spring with spring constant, $k_{h}$,
@@
 array backing is assumed to be stiff. The pad is attached to a linearly
-deformable leg, assumed to be another spring with spring constant,
+deformable leg (tibia), assumed to be another spring with spring constant,
 $k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
-array at a distance, $s$, from the right end of the array. The hinge, analogous to the tarsus-tibia (t-t) leg joint of an insect, 
+array at a distance, $s$, from the right end of the array. The hinge, analogous to the tibia-tarsus leg joint of an insect, 
 is at a vertical distance, $d_{s}$, from the surface. The hairs are
@@
 before pull-off, such that its pull-off force, $f_{p}=k_{h}\left(l_{h,p}-l_{h,0}\right)$.
-$F_{net}$ is the net force on the pad and $M_{net}$ is the the net
+$F_{net}$ is the net normal force on the pad and $M_{net}$ is the the net
 moment about the hinge, at a particular instant during the detachment
-process. The contact points between the hair and the surface is assumed to be laterally fixed due to high friction forces.
+process. We focus only on vertical detachment modes and thus lateral friction forces between the hairs and surface are not considered for our analysis.
 
@@
 \includegraphics{Figure1-model_schematic}\caption{\textbf{Spring contact model of a fibrillar adhesive pad.} The pad consists of
-an array of $N_{t}$ hairs connected to a deformable leg at the hinge.
+an array of $N_{t}$ hairs connected to a deformable leg at the joint.
 At a particular distance, $d_{s}$, $n$ number of hairs are in contact
@@
 where, $\Psi=s-\frac{n-1}{2}w$. For a particular value of $n$, equation
-\ref{eq:force_n_d} is valid until a certain distance, $d_{s,max}$,
+(\ref{eq:force_n_d}) is valid until a certain distance, $d_{s,max}$,
 above which the left most hair will detach. Just before detachment,
@@
 
-Equation \ref{eq:force_n_d} will be valid for $d_{s}\leq d_{s,max}$.
+Equation (\ref{eq:force_n_d}) will be valid for $d_{s}\leq d_{s,max}$.
 
@@
 
-We consider three possible mechanisms to detach the adhesive pad from
+We consider three tentative scenarios to detach the adhesive pad from
 a surface: 1) \emph{Fixed pull}, where the pad is pulled vertically
-up while keeping a fixed hinge (t-t leg joint); 2) \emph{Free pull,} where the
-pad is pulled vertically up while keeping the hinge (t-t leg joint) free to allow
+up while keeping a fixed joint; 2) \emph{Free pull,} where the
+pad is pulled vertically up while keeping the joint free to allow
 rotation of the array; 3) \emph{Flex}, where the pad is hinged
@@
 emulating the claw function in insects. To investigate each case in
-detail, let us assume a pad to be a one dimensional analogue of a 
+detail, let us assume a pad to be a one-dimensional analogue of a 
 dock beetle's adhesive pad \cite{RN19, RN79} with $N_{t}=25$ hairs and $\hat{f_{p}}=0.1$
-attached to a stiff leg (tibia) with $k_{l}\rightarrow\infty$. The situation
-of a soft leg (tibia) with $k_{l}/k_{h}=10$ is also considered for the first
+(see discussion on \emph{detachment pathways} for details) attached to a stiff leg (or tibia) with $k_{l}\rightarrow\infty$. The situation
+of a soft leg with $k_{l}/k_{h}=10$ is also considered for the first
 two cases involving vertical detachment.
@@
 \includegraphics{Case1-Fixed_pull}\caption{\textbf{Detachment by \emph{Fixed Pull}.} 
-Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a fixed hinge (tarsus-tibia leg joint). The
+Force-distance curves for a fibrillar adhesive pad, pulled vertically upwards with
+a fixed joint. The
 tilt angle, $\theta$, of the array is kept fixed during detachment.
 The leg (tibia) is either stiff ($k_{l}\rightarrow\infty$) or soft ($k_{l}/k_{h}=10$).
-Positive force values represent attraction. The green dashed line
+Positive force values represent attraction between the array and the surface. The green dashed line
 represents the maximum possible adhesion for the pad. All values are
@@
 while maintaining a constant tilt angle, $\theta$, with the surface.
-This can be achieved if the hinge (t-t leg joint) is kept fixed. 
+This can be achieved if the joint is kept fixed. 
 Equations \ref{eq:force_n_d}, \ref{eq:d_max}
 and \ref{eq:simul_detach} can be used to get the resulting force-distance
-curves.
+curves for such a scenario.
 
@@
 the individual hairs to detach distinctly rather than simultaneously,
-further reducing the net adhesive power of the array. We term this
+further reducing the maximum adhesion of the array. We term this
 effect of loss in adhesion due to a non-uniform hair deformation across
-the array as ``\emph{elastic weakening}''. When there is no tilt
+the array as \emph{elastic weakening}. When there is no tilt
 ($\theta=0\lyxmathsym{\textdegree}$), all the hairs undergo identical
-deformation and ultimately detaches simultaneously after a distance,
+deformation and ultimately detach simultaneously after a distance,
 $\hat{d_{s}}=0.1$. Here, no \emph{elastic weakening} occurs and the
@@
 force response. On further pulling, the hairs will start to detach
-sequentially from left to right, indicated by a characteristic ``saw-tooth''
+sequentially from left to right, indicated by a characteristic saw-tooth
 jitter in the force curves. The hairs of the pad with a higher tilt
@@
 tilt is the same as that for the stiff leg. The saw-tooth jitter are
-however minimized due to the leg's deformation, leading to a ``dampened''
+however minimized due to the leg's deformation, leading to a dampened
 force response. Interestingly, the force abruptly drops to zero for
@@
 This is an effect of the elastic recoil of the leg while each hair
-loses contact during the detachment process (equation \ref{eq:backing_deform}).
+loses contact during the detachment process (equation (\ref{eq:backing_deform})).
 The length difference between the detached hair just before it breaks
@@
 more than its maximum length ($l_{h,p}$), and thus will also detach,
-leading to further recoil of the leg. Equation \ref{eq:backing_deform}
+leading to further recoil of the leg. Equation (\ref{eq:backing_deform})
 shows that $\Delta l$ increases with every subsequent loss of hair
@@
 \includegraphics{Case2-Free_pull}\caption{\textbf{Detachment by \emph{Free Pull}.} 
-Force distance curves for a fibrillar adhesive pad, pulled vertically upwards with
-a free hinge (tarsus-tibia leg joint). $s$
-is the distance between the leg joint and the right end of the array
+Force-distance curves for a fibrillar adhesive pad, pulled vertically upwards with
+a free joint. $s$
+is the distance between the joint and the right end of the array
 and $L$ is the array length. The free joint allows further tilting
@@
 where the adhesive pad is pulled vertically upwards for detachment.
-However now, the leg joint is assumed to be free. In this case, the
-array will reorient itself to maintain a zero net torque about the
+However now, the joint is assumed to be freely movable. In this case, the
+array will reorient itself to maintain a zero net moment about the
 joint during the entire detachment process. At any given instant,
 the tilt angle, $\theta$, can be found by setting $M_{net}$ to zero
-in equation \ref{eq:moment_n_d} to get:
+in equation (\ref{eq:moment_n_d}) to get:
 
@@
 curves during a free vertical pull of the adhesive pad. Since the
-position of the leg joint will influence the net torque, we use the
+position of the joint will influence the net moment, we use the
 ratio, $s/L$, to study its effect on the detachment forces.
 
-Maximum adhesion is seen when the leg joint is positioned at the centre
+Maximum adhesion is seen when the joint is positioned at the centre
 of the array, i.e. $s/L=0.5$ (Figure \ref{fig:Free-pull}). Here,
-the net torque due to the hairs is balanced by symmetry and the array
+the net moment due to the hairs is balanced by symmetry and the array
 remains parallel to the substrate until all hairs detach simultaneously
@@
 away from the array centre leads to lower forces or adhesion. The
-resulting torque imbalance will tilt the array, which reduces the
+resulting moment imbalance will tilt the array, which reduces the
 net force due to the \emph{elastic weakening} effect, as described
-in the previous section. Higher $s/L$ increases the net torque to
+in the previous section. Higher $s/L$ increases the net moment to
 be balanced, leading to a higher tilt of the array and thus lower
@@
 jitter as the subsequent hairs detach in sequence. Nearly identical
-trend is seen for both a stiff and a soft leg. The elastic recoil
+trend is seen for both a stiff and a soft leg (tibia). The elastic recoil
 of the leg does slightly reduce the amplitude of the jitter for the
@@
 \begin{figure}[H]
-\includegraphics{Case3-Fixed_flex}\caption{\textbf{Detachment by flex.}
+\includegraphics{Case3-Fixed_flex}\caption{\textbf{Detachment by \emph{Flex}.}
 Force curves for a fibrillar adhesive pad detached by flexing it about the claw.
 $\hat{F}_{pull}=\frac{F_{pull}}{k_{h}w}$ is the normalised pulling
-force necessary to apply the torque about the claw-hinge for detachment,
+force necessary to apply the moment about the claw-hinge for detachment,
 $\hat{F}_{hinge}=\frac{F_{hinge}}{k_{h}w}$ is the normalised reaction
@@
 by rotating it about the claw-hinge, located outside the array. Such
-a mode of detachment will be driven by a torque applied by the leg
+a mode of detachment will be driven by a moment applied by the leg (tibia)
 to rotate the pad around the claw-hinge until all the hairs lose contact.
 Let $s_{h}$ be the distance between the claw-hinge and the right
-end of the array; $s_{l}$ be the distance between the fixed leg joint
-and the right end of the array. To illustrate the mechanism, let us
+end of the array; $s_{l}$ be the distance between the joint
+and the right end of the array. The joint is assumed to be fixed here. To illustrate the mechanism, let us
 fix $s_{l}/L=1$ and $s_{h}/w=10$ and vary the vertical claw-hinge
@@
 by the leg, $F_{pull}=M_{net}/\left(s_{l}+s_{h}\right)$, where $M_{net}$
-is obtained by setting $s=-s_{h}$ in equation \ref{eq:moment_n_d}.
-Equation \ref{eq:force_n_d} will give us the reaction force acting
+is obtained by setting $s=-s_{h}$ in equation (\ref{eq:moment_n_d}).
+Equation (\ref{eq:force_n_d}) will give us the reaction force acting
 on the claw-hinge, $F_{claw-hinge}$.
@@
 effect due to the inhomogeneous deformation of hairs. This results
-in a decrease in the net torque and thus lower $F_{pull}$ for smaller
+in a decrease in the net moment and thus lower $F_{pull}$ for smaller
 values of $d_{s}$. $F_{pull}$ can be further reduced of course by
@@
 from the surface following a given mechanism and $N_{t}f_{p}$ is
-the maximum possible adhesion of the pad (equation \ref{eq:simul_detach}).
+the maximum possible adhesion of the pad (equation (\ref{eq:simul_detach})).
 Reduction factor, $r$, represents the extent to which the adhesion
@@
 $\hat{f}_{p}$ influences the reduction factor under each mode of
-detachment (Figure \ref{fig:Reduction-factor_fp}). From the colour plots, 
-one can generally say that lower values of $\hat{f}_{p}$ increase
-the reduction factor and thus provide a greater possibility of controlling
-adhesion.
+detachment (Figure \ref{fig:Reduction-factor_fp}).
 
@@
 no influence on the reduction factor. On the other hand, shifting
-the position of the leg joint further away from the array (i.e. high
+the position of the joint further away from the array (i.e. high
 $s/L$) results in large values of $r$. In this scenario, the higher
-torque exerted by the array leads to a higher tilt, and thus increases
+moment exerted by the array leads to a higher tilt, and thus increases
 the reduction factor via \emph{elastic weakening}, saturating to the
@@
 and $\hat{d}_{s}$, with values as high as 100. Since this mode of
-detachment is driven by torque, the pulling force necessary to provide
-the torque can be decreased without any limit simply by having a long
-lever arm ($\hat{s}_{l}$). In contrast, for the previous cases of
-\emph{free pull} and \emph{fixed pull}, the reduction factor is capped
-to the maximum number of hairs in the array ($N_{t}=25$). Here, \emph{elastic
-weakening} can only reduce the array's adhesion force from $N_{t}$
+detachment is driven by moment, the pulling force necessary to provide
+the moment can be decreased without any limit simply by having a long
+lever arm ($\hat{s}_{l}$), i.e., with the joint positioned farther away from the array. 
+In contrast, for the previous cases of \emph{free pull} and \emph{fixed pull}, the reduction factor is capped to the maximum number of hairs in the array ($N_{t}=25$).
+Here, \emph{elastic weakening} can only reduce the array's adhesion force from $N_{t}$
 hairs down to a single hair at most.
@@
 The colour plots show that high $N_{t}$ increases $r$ irrespective
-of the mode of detachment. Under a tilted state, more number of hairs
+of the mode of detachment. Under a tilted state, more hairs
 are compressed when $N_{t}$ is high, which reduces the net adhesion.
 This highlights the advantage of having a split contact design found
-in many biological systems. Higher number of hairs offer a better
+in many biological systems. A higher number of hairs offers a better
 control over adhesion and thus is more suited for reversible attachment
@@
 Based on the three modes of detachment discussed in the previous sections,
-one can think of several strategies to detach a fibrillar adhesive pad
+one can think of several strategies to detach fibrillar adhesive pads
 from the surface. To illustrate this, let us consider the adhesive
 system of a dock beetle. The beetle is known to have 3 sets of hairy
-pads in each of their legs, each possessing hairs of different geometries.
+tarsal adhesive pads in each of their legs, each possessing hairs of different geometries.
 To keep our analysis simple, we will assume each leg to have only
-two pads, with identical hairs of ``mushroom'' geometry. The distal
+two adhesive pads, with identical hairs of mushroom-shaped geometry. The distal
 and proximal pads possess roughly 500 and 1000 hairs, respectively \cite{RN19}.
@@
 hairs, we can model this as a one-dimensional system of 20 and 40
-hairs, respectively, by combining the hairs along the width. Based
-on reported measurements \cite{RN79}, the beetle's ``combined hair''
+\emph{effective hairs}, respectively, by combining the hairs along the width. Based
+on reported measurements \cite{RN79}, the beetle's \emph{effective hair}
 is thus considered to have an effective pull-off force, $f_{p}=0.5\times25=12.5$
-\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N m\protect\textsuperscript{-1}.
+\textgreek{m}N and effective spring constant, $k_{h}=0.5\times25=12.5$ N m\protect\textsuperscript{-1}.
 The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
-long, spaced $w=10$ \textgreek{m}m apart. The adhesive pad also has
-a claw, around 200 \textgreek{m}m long, and the leg is connected roughly
-at the end of the proximal pad. This will put $\hat{s}_{h}=20$ and
+long, spaced $w=10$ \textgreek{m}m apart. At end of the tarsal segments, there is 
+a claw, around 200 \textgreek{m}m long, and the leg (tibia) is connected roughly
+at the end of the proximal tarsal pad. This will put $\hat{s}_{h}=20$ and
 $s_{l}/L=1$, measured relative to the right end of the distal pad.
 The beetle's leg is assumed to possess two joints which could serve
-as a hinges for rotation (H\textsubscript{1} and H\textsubscript{2}
+as a hinge for rotation during detachment (H\textsubscript{1} and H\textsubscript{2}
 in Figure \ref{fig:Detachment-pathways} inset). The claw can be used
-as an external hinge (H\textsubscript{3}) by flexing the pad around
+as an external hinge (H\textsubscript{3}) by flexing the tarsal pad around
 it.
@@
 initially the leg is pulled vertically up while keeping H\textsubscript{1}
-fixed, stretching the hairs. On reaching point $a$, H\textsubscript{1}
+fixed, stretching the hairs similar to path 1. On reaching point $a$, H\textsubscript{1}
 is set free, which results in a sudden drop in force due to the excess
-torque by the stretched hairs, tilting the array. Beyond this, the
+moment by the stretched hairs, tilting the array. Beyond this, the
 force curve follows the \emph{free pull} mechanism, with $\thicksim3.5$
@@
 \includegraphics{Detachment_pathways}\caption{\textbf{Beetle leg detachment pathways.}
-Force distance curves showing possible detachment pathways for a dock
-beetle's leg, derived from the spring contact model. The curves are
+Force curves showing the theoretical detachment pathways possible for a dock
+beetle's leg, as function of distance between the pad and the surface. The curves are
 offset laterally for clarity. Colours represent the distinct detachment
-pathways, as labelled correspondingly, with arrows indicating the
-direction of retraction. The different line style denotes the specific
+pathways, labelled as path 1 to 5, with arrows indicating the
+direction of retraction.
+Points a, b and c indicate instances of switching between the different detachment mechanisms for paths 3, 4 and 5 respectively (see text for details).
+The different line style denotes the specific
 detachment mechanism followed by any region of the pathway. The inset
-schematic shows the assumed locations of the different hinges (H\protect\textsubscript{1},
+schematic shows the assumed locations of the different joints or hinges (H\protect\textsubscript{1},
 H\protect\textsubscript{2} and H\protect\textsubscript{3}) employed
-by the leg.\label{fig:Detachment-pathways}}
+by the leg. \label{fig:Detachment-pathways}}
 \end{figure}
@@
 adhesive pads is suitable for modulating its adhesion. Effective control
-and release of its leg joints can help the insect to reduce the pad's
+and release of its joints can help the insect to reduce the pad's
 adhesion, allowing it to detach with little effort. High reduction
@@
 best of our knowledge, there is no direct experimental evidence that
-beetles can modulate its adhesion by taking advantage of this effect.
+beetles or any other animal can modulate its adhesion by taking advantage of this effect.
 Considering that hair deformation occurs at length scales below 10
@@
 beetles \cite{RN83}, we argue that the following experimental observations
-provide support to our proposed theory: 1) The detachment was shown
+provide support to our proposed model: 1) The detachment was shown
 to follow a three-dimensional twist of the leg, which suggests a complex
 inhomogeneous deformation of hairs across the array, leading to \emph{elastic
-weakening}, which is suited for easy detachment. 2) The beetle can at times instantaneously detach all
-its legs and ``drop'' itself while upside down. This could be explained
-by the beetle freeing up its leg joints and using just its body weight
+weakening}, which is suited for easy detachment.
+Similar twisting action during detachment was also observed in flies \cite{niederegger2003} and has been used to easily detach mushroom-shaped artificial adhesive arrays \cite{kang2017}.
+2) The beetle can at times instantaneously detach all
+its legs and drop itself while upside down. This could be explained
+by the beetle freeing up its joints and using just its body weight
 to provide the necessary force to detach all its legs via \emph{free
@@
 the hairs, both leading to a reduction in adhesion for easy detachment.
-4) Contact images showed that the array ``peels'' from the proximal
+4) Contact images showed that the array \emph{peels} from the proximal
 to distal direction during detachment. However, the beetle's hairs
 are attached to a relatively stiff backing \cite{RN53}, so it wouldn't
-be able to ``peel'' its array, since peeling, strictly speaking,
+be able to \emph{peel} its array, since peeling, strictly speaking,
 depends on the elastic contribution of a thin flexible backing as
-it bends during the process \cite{RN147}. Rather, the ``peeling''
+it bends during the process \cite{RN147}. Rather, the \emph{peeling}
 observed in the beetle's case should be a result of the pad detaching
@@
 
+Our analysis had been limited to normal forces during detachment.
+A similar analysis considering the energy required to detach the array will however not yield any \emph{elastic weakening} effect.
+Since we had assumed a purely elastic system, the initial and final energy of the system would be the same regardless of the mode of detachment, and thus the work of adhesion would remain identical in all scenarios.
+The reduction of adhesion force is however advantageous since an insect wouldn't then need a strong muscular to system to detach its legs, which are typically capable of attachment forces several times its body weight \cite{ENDLEIN2007}.
+
 \section{Conclusion}
@@
 Inhomogeneous deformation of hairs results in significant reductions
-in the adhesion of a fibrillar system. Such a condition can be achieved
+in the adhesion of a fibrillar system similar to an insect's tarsal hairy adhesive pads. Such a condition can be achieved
 by either 1) pulling the pad while maintaining a constant tilt angle,
-2) pulling the pad while maintaining a free leg joint or 3) flexing
+2) pulling the pad while maintaining a free tibia-tarsus leg joint or 3) flexing
 the pad around the claw. Strategic control of the joint's mobility or claw
@@
 design conditions to maximize the range of control over adhesion.
-The proposed theory is supported by previously reported experimental
-observations of leg detachment in dock beetles and highlights possible role of the leg joint and claws to 
+The proposed model is supported by previously reported experimental
+observations of leg detachment in dock beetles and highlights possible role of the joint and claws to 
 enable reversible adhesion. Similar strategies could potentially be adopted in the design of bio-inspired 
@@
 
-The net torque about the joint due to the deformed hairs of the array
+The net moment about the joint due to the deformed hairs of the array
 is,

### 2022-08-24 review/manuscript.tex
Revised version JTB finished and sent
finished review of JTB referee comments
added new figure for reduction factor with parameter chi
manuscript changed manuscript

--- 2022-08-13 source/tex/manuscript.tex
@@
 
-Simplifying, we get (see Appendix A for derivation):
+Simplifying, we get (see Appendix B for derivation):
 
@@
 The net moment, $M_{net}$, about the joint can be similarly derived
-(see Appendix A):
+(see Appendix B):
 
@@
 \[
-\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{w}
+\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{L}
 \]
@@
 on the reduction factor for each mode of detachment. Here, we fix
-the number of hairs, $N_{t}=25$. All values are normalized to dimensionless
-forms, as described in text. \label{fig:Reduction-factor_fp}}
+the number of hairs, $N_{t}=25$. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and 
+$\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor_fp}}
 \end{figure}
@@
 the reduction factor for each mode of detachment. Here, we fix the
-dimensionless parameter, $\hat{f}_{p}=0.1$. All values are normalized
-to dimensionless forms, as described in text. \label{fig:Reduction-factor-Nt}}
+dimensionless parameter, $\hat{f}_{p}=0.1$. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and $\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor-Nt}}
 \par\end{centering}
 \end{figure}
+
+Figures \ref{fig:Reduction-factor_fp} and \ref{fig:Reduction-factor-Nt} can be combined into a single set of colour plots by defining a new dimensionless parameter,  $\chi=\hat{f}_{p} N_{t}=\frac{f_{p}N_{t}}{k_{h}w}$ (see Appendix A).
+Overall, we see that \emph{flex} mode of detachment shows the highest reduction factor among the three modes, with the optimal value of $\chi \sim 1$.
 
@@
 which will further limit the reduction in adhesion due to the smaller
-effective modulus. Thus, the geometry of the individual hairs is also
-crucial in effectively reducing adhesion by \emph{elastic weakening}.
-Ideally, hairs with large diameters would be preferable to eliminate
-buckling, and optimally long hairs would provide a large range of
-angles to which the pad can be tilted while avoiding bundling.
+effective modulus. Buckling could also, interestingly, promote easier detachment in the \emph{free pull} mode.  
+When the compressed hairs at one end of the array buckle, 
+there would be an excess clockwise moment in the array system (Figure \ref{fig:Free-pull}). 
+This excess moment could subsequently drive the detachment of the remaining hairs.
+In the case of biological systems, the ability of an insect to provide the load necessary to tilt and compress its hairy adhesive pad against the surface would further introduce limitations to follow any of the detachment modes discussed here.
+All things considered, the geometry and elastic properties of the individual hairs are 
+crucial parameters to consider in the design of an optimal array system which shows reversible adhesion via \emph{elastic weakening}.
 
@@
 
+\section{{Reduction factor: master plot}}
+
+\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
+\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}}
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics{Reduction_factor-chi}\caption{\textbf{Effect of $\chi$ on reduction factor.} 
+Here, we define a unified dimensionless design parameter $\chi=\frac{f_{p}N_{t}}{k_{h}w}$, combining $\hat{f}_{p}$ and $N_{t}$ into a single number.
+The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and $\hat{s}=\frac{s}{L}$, as described in text.
+\label{fig:Reduction-factor-chi}}
+\par\end{centering}
+\end{figure}
+
 \section{{Derivations}}
@@
 %\subsection{Derivations}
-
-\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
-\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}}
 

### 2022-09-24 source/tex/manuscript.tex
referee 2 comments responded and revision submitted

@@
 to the stored elastic energy. Suppose the leg relaxes upward by a
-recoil length, $\Delta l$. For $n$ hairs in contact, the force balance
-before and after a hair detaches is given respectively by:
+recoil length, $\Delta l$, at the point of the joint. For $n$ hairs in contact, when a hair detaches, 
+the array's tilt angle will change from initial $\theta_{b}$ to $\theta_{a}$ as a result of joint rotation. 
+The $i^{th}$ hair of the array thus deforms by $\Delta l_{i}$, which by geometry, is derived as:
+\begin{equation}
+\Delta l_{i}=\Delta l + iw\left(\tan \theta_{a}-\tan \theta_{b}\right)\label{eq:delta_li}
+\end{equation}
+
+ The force balance before and after a hair detaches is thus given respectively by:
 
@@
 \stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)=k_{l}\left(l_{l}-l_{l,0}\right)\\
-\stackrel[i=1]{n-1}{\sum}k_{h}\left(l_{h,i}+\Delta l-l_{h,0}\right)=k_{l}\left(l_{l}-\Delta l-l_{l,0}\right)
+\stackrel[i=1]{n-1}{\sum}k_{h}\left(l_{h,i}+\Delta l_{i}-l_{h,0}\right)=k_{l}\left(l_{l}-\Delta l-l_{l,0}\right)
 \end{array}
@@
 
-Solving the above two equations for $\Delta l$, we get:
+Solving the above two equations with equation \ref{eq:delta_li} for $\Delta l$, we get:
 
 \begin{equation}
-\Delta l=\frac{f_{p}}{k_{h}\left(n-1\right)+k_{l}}\label{eq:backing_deform}
+\Delta l=\frac{f_{p}-k_{h}w(n/2)(n-1)\left(\tan \theta_{a}-\tan \theta_{b}\right)}{k_{h}\left(n-1\right)+k_{l}}\label{eq:backing_deform}
 \end{equation}
@@
 force values represent attraction by convention.
+Python scripts were written to solve the above equations under specific detachment conditions (available in the public repository \url{https://github.com/PranavSudersan/paper-effect_of_tilt/blob/main/codes/Fibrillar\%20adhesion\%20-\%20Effect\%20of\%20tilt.ipynb})
 
@@
 curves for such a scenario.
+To summarize the numerical procedure in brief, we start with an initial $n=25$ hairs.
+${F}_{net}$ is then calculated for increasing ${d_{s}}$, until $d_{s}= d_{s,max}$, upon which $n$ value is decremented by 1.
+The above process is repeated for increasing $d_{s}$ until $n=0$, indicating complete detachment.
+For the case of the soft leg, on each instance when $n$ is decremented,  ${d_{s}}$ is increased by an additional $\Delta l$ value (equation \ref{eq:backing_deform}) in order to account for the recoil effect of the leg.
 
@@
 sequentially from left to right, indicated by a characteristic saw-tooth
-jitter in the force curves. The hairs of the pad with a higher tilt
-angle will start to detach first, followed by the ones with a lower
+jitter in the force curves. The pad with a higher tilt
+angle initiates hair detachment first, in comparison to a pad with a lower
 tilt.
@@
 shows that $\Delta l$ increases with every subsequent loss of hair
-contact if $\theta$ is kept constant. This implies that, once initiated,
+contact if $\theta$ is kept constant (i.e. $\theta_{b}=\theta_{a}$). This implies that, once initiated,
 the leg's recoil will always be large enough to detach every remaining
@@
 \ref{eq:d_max} and \ref{eq:simul_detach}, we can find force-distance
-curves during a free vertical pull of the adhesive pad. Since the
+curves during a free vertical pull of the adhesive pad. 
+A similar numerical procedure as \emph{fixed pull} is followed here. Since the
 position of the joint will influence the net moment, we use the
@@
 soft leg case. However, no abrupt drop in the force is seen like before.
-As the hairs detach, the array gets tilted more and more, making it
-less likely for the recoil length, $\Delta l$, to exceed $w\sin\theta$
+As the hairs detach, the array gets tilted more and more (i.e. $\theta_{b}<\theta_{a}$), making it
+less likely for the recoil length, $\Delta l$, to exceed $w\sin\theta_{a}$
 and detach the next adjacent hair. Thus here, we don't see any propagation
@@
 and the right end of the array. The joint is assumed to be fixed here. To illustrate the mechanism, let us
-fix $s_{l}/L=1$ and $s_{h}/w=10$ and vary the vertical claw-hinge
+fix $s_{l}/L=1$ (here, $L=24w$) and $s_{h}/w=10$ and vary the vertical claw-hinge
 distance, $d_{s}$. At any particular instant, the pulling force applied
@@
 For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
-implying that the claw should adhere well with the surface to resist
+implying that the claw should stick well with the surface, perhaps by mechanical interlocking, to resist
 this negative load. As the detachment progresses however, the array
@@
 are compressed when $N_{t}$ is high, which reduces the net adhesion.
-This highlights the advantage of having a split contact design found
-in many biological systems. A higher number of hairs offers a better
-control over adhesion and thus is more suited for reversible attachment
+This highlights another advantage of having a split contact design found
+in many biological systems. A design comprising of a large number of hairs not only enhances the adhesion due to scaling effects \cite{Kamperman2010}, but could also offer a better
+control over adhesion, making it quite suitable for reversible attachment
 and detachment during locomotion. The specific trends of reduction
@@
 to provide the necessary force to detach all its legs via \emph{free
-pull} (similar to path 3 above). 3) Only a fraction of the beetle's
+pull} (similar to path 3 above).
+Lateral video recordings showed that in this scenario, claws were the last to detach when a leg loses contact with the surface, which also indicates a \emph{flex} mode of detachment (similar to path 5).
+3) Only a fraction of the beetle's
 pads made contact with the surface during locomotion, which indicates
@@
 
-Inhomogeneous deformation of hairs results in significant reductions
-in the adhesion of a fibrillar system similar to an insect's tarsal hairy adhesive pads. Such a condition can be achieved
+Controlled detachment of a fibrillar system similar to an insect's tarsal hairy adhesive pads can be achieved
 by either 1) pulling the pad while maintaining a constant tilt angle,
 2) pulling the pad while maintaining a free tibia-tarsus leg joint or 3) flexing
-the pad around the claw. Strategic control of the joint's mobility or claw
+the pad around the claw. In all three scenarios, an inhomogeneous deformation of hairs across the array results in significant reductions
+in the net adhesion due to an elastic effect. Strategic control of the joint's mobility or claw
 can allow the leg to easily switch between the above mechanisms, thus
@@
 design conditions to maximize the range of control over adhesion.
-The proposed model is supported by previously reported experimental
+The proposed model has been compared with previously reported experimental
 observations of leg detachment in dock beetles and highlights possible role of the joint and claws to 
